### 2017-02-16 ms.tex
added tex, figs, pdf

%-------------------------------------------------------------------------------
% Kyle Westfall
% westfall@ucolick.org
% UCO/Lick Observatory
% University of California, Santa Cruz
% 1156 High St.
% Santa Cruz, CA 95064
% USA
%
% VERSION:
%       05 Feb 2017: (KBW) v01: stab in the dark
%
% SUBMITTED:
%
%-------------------------------------------------------------------------------

\input{../dm_nomenclature/dmnom_rv4.tex}

\documentclass[apj,iop,revtex4,numberedappendix]{emulateapj}
\RequirePackage{calc}
\usepackage{natbib}
\usepackage{url}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{graphicx}
\bibliographystyle{apj}

\slugcomment{Draft: 14 Feb 2017}

\shortauthors{Westfall et al.}
\shorttitle{Asymmetric Drift across the Blue Cloud}

\begin{document}

\title{ The trend in asymmetric drift across the blue cloud }

\author{ Kyle B. Westfall\altaffilmark{1}, Matthew A.
Bershady\altaffilmark{2}, Kevin Bundy\altaffilmark{1}, et al. }

\altaffiltext{1}{UCO/Lick Observatory, University of California, Santa
Cruz, 1156 High St., Santa Cruz, CA 95064, USA}

\altaffiltext{2}{Department of Astronomy, University of Wisconsin-Madison, 475
N. Charter St., Madison, WI 53706, USA}

\email{westfall@ucolick.org}

\begin{abstract}

Using the statistical prowess of the SDSS-IV/MaNGA survey, we
demonstrate a strong trend between the strength of lag of the stellar
rotation curve behind that of the ionized gas as a function of its
absolute luminosity.

\end{abstract}

\keywords{ galaxies: kinematics and dynamics --- galaxies: spiral ---
galaxies: structure }

\section{ Motivation }
\label{sec:intro}

Asymmetric drift is the lag of the ensemble stellar rotation speed
behind the circular speed defined by the gravitational potential.  For
stellar ensembles, \citet[][Section 4.4.3]{2008gady.book.....B} provide
an intuitive description of asymmetric drift as arising due to the
combined effect of the radially decreasing surface-density and
velocity-dispersion profiles typical of axisymmetric systems.  Using the
$v_R$ moment of the collisionless Boltzmann equation, one obtains the
Jeans (ref) equation that directly relates the circular speed ($v_c$),
the mean stellar tangential speed ($\overline{v_\theta}$), and the
stellar velocity ellipsoid (SVE) as a function of radius in the plane of
symmetry:
%
\begin{equation}
%
v_c^2 - \overline{v_\theta}^2 = \sigma_R^2\left[
\frac{\sigma_\theta^2}{\sigma_R^2} -
\frac{R}{\rho\sigma_R^2}\frac{\partial(\rho\sigma_R^2)}{\partial R} -
1\right] - R\frac{\partial\overline{v_R v_z}}{\partial z},
%
\label{eq:adformal}
%
\end{equation}
%
where $R,\theta,z$ are the cylindrical coordinates, $\rho$ is the volume
density, and $\sigma$ is the velocity dispersion.  Along with the
standard assumptions of dynamical equilibrium and negligible radial and
vertical flows inherent to its derivation, equation \ref{eq:adformal} is
often simplified by assuming the right-most term --- describing the
covariance between the radial and vertical motions as a function of
perpendicular distance to the plane of symmetry --- is negligible (cf.
Cuddeford \& Amendt).

Asymmetric drift has been measured in numerous systems.  Perhaps most
notably, e.g., Dehnen \& Binney have shown that populations of stars
show a direct correlation between their velocity dispersion and the
degree to which their mean rotation speed lags behind that of the Local
Standard of Rest (LSR), much in line with the expectation provided by
equation \ref{eq:adformal}.  Although there have been some studies of
asymmetric drift in external galaxies (refs), it is often treated as a
nuisance phenomenon that must be corrected for when trying to constrain
the circular speed curve of a galaxy (refs).  The ubiquity and
phenomenology of asymmetric drift as a salient observable has not yet
been studied for a statistically significant population of galaxies.
Our aim is therefore to provide a first look at the correlation between
asymmetric drift measurements and basic broad-band photometric
properties for a large sample of galaxies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
%
\begin{center}
%
\includegraphics[width=0.8\textwidth]{figs/cmd_flux.pdf}
%
\end{center}
%
\caption{
%
${\rm N} - r$ color and absolute $i$-band magnitude ($M_i$) for all
galaxies observed during the first two years of the MaNGA Survey (left),
the subsample of galaxies {\em not} selected to be kinematically regular
(middle; see text), and the asymmetric-drift sample used throughout the
remainder of our analysis.  The color of the data points in the top row
represent the mean H$\alpha$ surface brightness [[check aperture]]
according to the colorbar to the right; the bottom row replaces the
color by the $r$-band surface brightness density.
%
}
%
\label{fig:sample}
%
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In addition to the basic understanding of this dynamically relevant
quantity, our interest in asymmetric drift stems from its fundamental
dynamical connection to the full phase-space distribution function of a
galaxy's stars, as empirically demonstrated in the Milky Way.  Indeed,
Westfall et al. (2011) (see also refs) used asymmetric drift to
constrain the axial ratios of the SVE given direct measurements of the
line-of-sight (LOS) stellar velocity dispersion, $\sigma$.
Alternatively, if one can statistically constrain the shape of the SVE
(refs), measurements of asymmetric drift could be used as a proxy for
stellar $\sigma$ by either appealing to equation \ref{eq:adformal} or an
empirical relation calibrated by samples with both asymmetric drift and
$\sigma$ measurements.  Such a use of asymmetric drift as a proxy for
stellar $\sigma$ is attractive in the low-surface-brightness and
low-velocity-dispersion regimes where direct measurements are difficult
and/or expensive.  We commit to this paradigm by using the following
nomenclature for asymmetric drift, following from equation
\ref{eq:adformal}:
%
\begin{equation}
%
\sigma_a^2 \equiv v_c^2 - \overline{v_\theta}^2.
%
\label{eq:addef}
%
\end{equation}

For disk galaxies, there is a decades-long industry of using cold-gas
tracers to construct circular-speed curves of galaxies (refs).  These
data have provided the first concrete arguments for the presence of
massive dark-matter halos (ref) based on mass model reconstruction
(refs) and have formed the basis for the most robust Tully-Fisher
relations compiled for the local Universe (refs).  However, it is
important to acknowledge that one cannot directly measure $v_c$,
effectively making $\sigma_a$ unobservable.  That is, every dynamical
tracer has some non-zero dynamical pressure such that it will lag behind
the theoretically defined circular speed.  There are very clear examples
of early-type galaxies that show differential asymmetric-drift in their
molecular (e.g., CO), atomic (e.g., \ion{H}{1}), and/or ionized
(H$\alpha$) tracers relative to a robust mass model of $v_c$ (Davis et
al.) due to the different turbulent/thermal pressures intrinsic to these
tracers.  However, these signatures are much less apparent in disk
galaxies.  For example, Martinsson et al.\ show that H$\alpha$ and
\ion{H}{1} rotation curves are consistent for the DiskMass Survey within
the limits of their constraints on beam-smearing, suggesting that any
correction for the lag of either behind the circular speed should be
small.  Indeed, theoretical calculations (Dalcanton \& Stilp) suggest
that gas-pressure corrections to \ion{H}{1} rotation curves should be
largely negligible for galaxies with ${\mathcal M} > 10^x {\mathcal
M}_\odot$.  Nevertheless, we emphasize here that our measurements of
$\sigma_a$ may be better termed as a {\em differential tangential lag}
because they are based on the quadrature difference between the observed
H$\alpha$ and stellar rotation curves in our galaxy sample (Section
\ref{sec:data}).  These measurements are perfectly valid in their own
right; however, it is their interpretation in the context of the
theoretical definition of asymmetric drift that should be questioned in
some regimes, as discussed in Section \ref{sec:discussion}.

We present the data used for our analysis in the following section.  In
Section \ref{sec:results}, we demonstrate that there is a strong
correlation between the absolute $i$-band magnitude of a galaxies and
the strength of its asymmetric drift measured at half of an effective
radius (0.5 $R_{\rm eff}$).  We also illustrate the weak color
dependence in this relation.  We summarize and discuss these results in
Section \ref{sec:discussion}.

\section{Data}
\label{sec:data}

We use integral-field spectroscopy from the SDSS-IV/MaNGA (Mapping
Nearby Galaxies from APO) Survey to construct stellar and ionized-gas
velocity fields for 2715 unique galaxies, 39 of which have multiple
observations.  The kinematic measurements are provided by the MaNGA data
analysis pipeline (DAP; Westfall et al., in prep): the ionized-gas
kinematics are based on simple single-Gaussian fits to the H$\alpha$
emission feature and the stellar kinematics are determined using pPXF
(Cappellari et al.) with the MILES stellar template library (Jesus FB et
al.).

The MaNGA galaxy selection (Wake et al. in prep) is a simple cut in
absolute $i$-band magnitude, $M_i$, and redshift, $z$, and provides a
complete sampling of the overall galaxy population.  As such,
measurements of stellar and/or H$\alpha$ rotation curves for some
systems will be difficult/impossible.  Using the photometry from the
NASA-Sloan Atlas (ref),\footnote{\url{nsatlas.org}} Figure
\ref{fig:sample} shows the color-magnitude diagram of all galaxies
colored by their mean H$\alpha$ and $r$-band surface brightness.
[[TODO: Need to check this plot.]] Although not excluded from our
velocity-field analysis {\em a priori}, we expect to obtain poor
rotation curve measurements for galaxies with low H$\alpha$ and stellar
surface brightness.\footnote{
%
The uniformity of the MaNGA survey (Law et al. 2015) is such that S/N is
tightly correlated with surface brightness.}

[[Extinction corrections for the CMD?]]

We model the geometric projection of the rotational plane of each galaxy
using the approach presented by Andersen \& Bershady (2013); see also
Westfall et al. (2011).  In three independent fitting iterations, the
model fits are optimized for the H$\alpha$ velocity field, the stellar
velocity field, and simultaneously for both data sets; for the latter,
the geometry is forced to be the same for the two dynamical tracers, but
the parametrized rotation curves are independent.  We use these
velocity-field-fitting results to objectively isolate a set of
``kinematically regular'' galaxies.  Briefly, galaxies in this sample
must have: (i) successful velocity-field fits for all three approaches,
(ii) differences in the measured H$\alpha$ and stellar systemic velocity
of less than 20 \kms, (iii) dynamical centers that are consistent to
within a fiber diameter of the morphological center [[check]], (iv)
H$\alpha$ and stellar velocity-field position angles that are consistent
to within $\pm$15$\arcdeg$, and (v) kinematic inclinations between
$15\arcdeg < i < 80\arcdeg$ that are both consistent between the
H$\alpha$ and stellar data and with respect to the photometric
ellipticity to within $\pm$20$\arcdeg$.  The constraint on the
inclination is by far the most stringent. [[give number of galaxies cut
by each criterion?]]  Applying these constraints yields a sample of 798
observations (for 790 unique galaxies) out of the 2764 observations
analyzed.  Eleven galaxies with repeat observations satisfy the
selection criteria; however, only five of these show all observations
are consistently selected, whereas the other six show one or more of the
observations did not pass our constraints [[we should understand
this.]].  [[TBD: Finally, we also visually inspected the broad-band
imaging of these 790 galaxies and eliminated merging and highly
extincted (highly inclined) systems yielding a final sample of XXX
galaxies.]]  We hereafter refer to galaxies that satisfy our selection
criteria as the ``asymmetric-drift'' sample.

Figure \ref{fig:sample} shows the color-magnitude distribution for all
MaNGA galaxies, as well as the distributions of those galaxies included
and excluded from our asymmetric-drift sample.  As expected, galaxies
with relatively high H$\alpha$ and $r$-band surface brightness are
preferentially selected, excluding much of the red sequence as well as
the brightest and faintest galaxies in the blue cloud.  Although the
conclusions we reach based on our asymmetric drift sample are
astrophysically meaningful, it is important to appreciate the biased
representation of the overall galaxy population represented by the
sample in our analysis.  [[Show histogram of kinematically regular
sample against the volume-corrected distribution of the MaNGA parent
sample in Mi and N-r, and discuss.]]

Our velocity-fitting method provides a model rotation curve fit to both
the H$\alpha$ and stellar data, each parametrized as a hyperbolic
tangent function: $v_{\rm rot} = v_{\rm flat} \tanh(R/h_v)$.  However,
our primary result is based on the error-weighted mean of the
deprojected rotation curve measurements for each dynamical tracer within
$\pm$30$\arcdeg$ of the major axis and $2\farcs5$ radial bins centered
at 0.25, 0.5, 0.75, 1.0, and 1.25 $R_{\rm eff}$ --- $R_{\rm eff}$ is the
effective radius using the elliptical Petrosian analysis from the
NASA-Sloan Atlas. [[Check that $R_{\rm eff}$ includes the multiplicative
offset to match these Petrosian and Sersic $R_{\rm eff}$ in the mean.]]
Specifically, we calculate the error-weighted mean and standard
deviation of $v_j = V_j/\cos\theta_j/\sin i$ and
%
\begin{equation}
%
\sigma_{a,j}^2 = (V_{{\rm H}\alpha,j}^2 - V_{\ast,j}^2) (\cos\theta_j
\sin i)^{-2},
%
\label{eq:dproj}
%
\end{equation}
%
where $V_j$ is the LOS measurement of each component in spaxel $j$
located at the in-plane polar coordinates $R_j$ and $\theta_j$ and $i$
is the disk inclination.

[[An example demonstrating the details of our measurements is
illustrated in Figure X.]]

We calculate errors in $v_{{\rm H}\alpha}$ and $\sigma_a$ as the
quadrature sum of the error-weighted standard error (i.e., the
error-weighted standard deviation divided by $\sqrt N$) and the
propagated error in the error-weighted mean. [[Can revisit this.
Details of error calculation not all that important.  We're dominated by
intrinsic deviations from the regression.]]

\section{Results}
\label{sec:results}

\begin{figure}
%
\begin{center}
%
\includegraphics[width=1.0\columnwidth]{figs/mi_models.pdf}
%
\end{center}
%
\caption{
%
Global photometry measurements versus kinematics measurements at
$R=R_{\rm eff}$ for the asymmetric-drift sample: $M_i$ versus (a) $N-r$
color with each point colored according to $\sigma_a^2$, (b) $v_{{\rm
H}\alpha}$ with each point colored according to $\sigma_a^2$, (c)
$\sigma_a^2$ with each point colored according to $v_{{\rm H}\alpha}$,
and (d) $\sigma_a/v_{{\rm H}\alpha}$ with each point colored by the
$N-r$ color.  Panels (b), (c), and (d) include the Spearman rank
correlation coefficient, $r_s$, and the linear regressions (solid lines)
constructed from the median parameters provided in Table
\ref{tab:lines}.  The dashed lines are offset from linear regression by
the modeled intrinsic scatter in the relation ($\varepsilon_y$).
%
}
%
\label{fig:correlation}
%
\end{figure}

Figure \ref{fig:correlation}(a) shows the $(M_i, N-r)$ color-magnitude
diagram (see right column of Figure \ref{fig:sample}) with the points
colored according to $\sigma_a$ measured at $R=0.5R_{\rm eff}$.  There
is a clear trend where brighter galaxies have larger $\sigma_a$; the
remainder of the Figure examines this trend.

We plot $M_i$ versus $v_{{\rm H}\alpha}$, $\sigma_a^2$, and
$\sigma_a/v_{{\rm H}\alpha}$ in Figures \ref{fig:correlation}(b),
\ref{fig:correlation}(c), and \ref{fig:correlation}(d), respectively.
The points are colored according to the color bar and quantity to the
right of each panel.  Each panel provides the Spearman rank correlation
coefficient, $r_s$, of the plotted data with errors derived from $10^3$
bootstrap simulations.  We have also used a Markov Chain Monte Carlo
(refs) to sample the Bayesian posterior distribution for a linear
regression to the data in each panel, incorporating the errors in both
axes (refs); the errors in the kinematic quantities are always dominant.
The fitted model is a line in parametric form with an intrinsic Gaussian
scatter perpendicular to the line.  That is, the line is defined as
$\mathbf{l}(t) = \mathbf{l}_0 + t\ \hat{\mathbf{l}}$ for a generalized
coordinate $t$ along the line, an origin $\mathbf{l}_0 = \{x_0, y_0\}$,
and the unit vector $\hat{\mathbf{l}} = \{\cos\phi, \sin\phi\}$.  The
fitted parameters are $y_0$, $\phi$, and the dispersion of the intrinsic
Gaussian scatter about the line, $\varepsilon$; $x_0$ is fixed at the
median abscissa of the data being fitted ($x_0 = M_{i,0} = -20.6$).
Uniform priors are used for $y_0$ and $\phi$ and a logarithmic prior
[[check]] is used for $\varepsilon$ (ref).  Using the returned samples
of the posterior, we also provide parameters for the slope-intercept
form of the line --- $y = mx + b$ where $m = \tan\phi$ and $b = y_0 -
x_0 \tan\phi$ --- and the scatter projected along the ordinate,
$\varepsilon_y = \varepsilon/|\cos\phi$|.  Table \ref{tab:lines}
provides the median and standard deviation of the marginalized
distribution of each parameter; these parameters have been used to
construct the lines provided in Figure \ref{fig:correlation}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable}{ c r r r }
\tabletypesize{\small}
\tablewidth{0pt}
\tablecaption{Linear Regressions for $M_i$
    [[Check slope-intercept form]]}
\tablehead{ & \multicolumn{3}{c}{Dependent Variable} \\
    \cline{2-4} \\[-3pt]
 \colhead{Parameter} & \colhead{$v_{{\rm H}\alpha}$} &
 \colhead{$\log(\sigma_a^2)$} &
 \colhead{$\log(\sigma_a/v_{{\rm H}\alpha})$} }
\startdata
          $y_0$ &      2.168 &       3.78 &     -0.269 \\
                & $\pm$0.003 &  $\pm$0.01 & $\pm$0.003 \\[2pt]
         $\phi$ &     170.70 &      160.1 &      -0.24 \\
                &  $\pm$0.15 &   $\pm$0.5 &  $\pm$0.17 \\[2pt]
  $\varepsilon$ &      0.069 &      0.209 &      0.068 \\
                & $\pm$0.001 & $\pm$0.005 & $\pm$0.002 \\[2pt] \hline \\[-4pt]
            $m$ &     -0.164 &     -0.362 &     -0.004 \\
                & $\pm$0.003 & $\pm$0.009 & $\pm$0.003 \\[2pt]
            $b$ &      -1.20 &      -3.69 &      -0.36 \\
                &  $\pm$0.05 &  $\pm$0.19 &  $\pm$0.06 \\[2pt]
$\varepsilon_y$ &      0.070 &      0.222 &      0.068 \\
                & $\pm$0.001 & $\pm$0.005 & $\pm$0.002
\enddata
\label{tab:lines}
\end{deluxetable}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As expected, there is a strong correlation between $v_{{\rm H}\alpha}$
and $M_i$.  However, it is important to note that Figure
\ref{fig:correlation}(b) does not present the Tully-Fisher (ref)
relation for our asymmetric-drift sample; the Figure gives the rotation
speed at $R=0.5R_{\rm eff}$, not a measure of the full-width of the
dynamically broadened line profile.  The slope of the relation in Figure
\ref{fig:correlation}(b) is steeper than a nominal Tully-Fisher relation
because galaxies at low luminosity tend to have more slowly rising
rotation curves (refs), which can be confirmed by plotting $h_{v,{\rm
H}\alpha}/R_{\rm eff}$ as a function of $M_i$. [[actually show this?]]

Figure \ref{fig:correlation}(c) gives the direct representation of the
gradient in the point color seen in Figure \ref{fig:correlation}(a).
The data in this panel are highly correlated, both as determined by
$r_s$ and the fitted regression.  The intrinsic scatter increases from
0.07 dex (17\%) in $(M_i,v_{{\rm H}\alpha})$ to 0.21 dex (62\%) in
$(M_i,\sigma_a^2)$; however, this is close to the $\sim$0.1 dex scatter
if considering $(M_i,\sigma_a)$ instead.

If $\sigma_a$ or $v_{{\rm H}\alpha}$ was a secondary parameter in the
distribution of $(M_i,v_{{\rm H}\alpha})$ or $(M_i,\sigma_a^2)$,
respectively, we should expect a gradient in the point color in Figures
\ref{fig:correlation}(b) and \ref{fig:correlation}(c) {\em
perpendicular} to the fitted regression.  However, we see that the
primary gradient in point color is parallel to the fitted regression.
This is consistent with the result that there is little to no
correlation between $M_i$ and $\sigma_a/v_{{\rm H}\alpha}$, as shown in
Figure \ref{fig:correlation}(d):  Both $r_s$ and $\phi$ are small and
only marginally significant with respect to their errors.  From equation
\ref{eq:dproj}, this implies that the deprojected stellar rotation is a
roughly constant fraction of the ionized-gas rotation speed, with
$v_{\ast} \sim 0.9 v_{{\rm H}\alpha}$.  Although the radius at which the
asymmetric drift was sampled is different, this ratio is consistent with
galaxies from the DiskMass survey (Martinsson et al.).

The points in Figure \ref{fig:correlation}(d) are colored by the global
$N-r$ color; however, it is difficult to determine from this
illustration if their is any correlation between $\sigma_a/v_{{\rm
H}\alpha}$ and global galaxy color.  One might expect such a correlation
if, for example, galaxies with different global color different
light-weightings of the thin vs. thick-disk (refs [[not sure there are
relevant ones]]), which propagates to a different dominant dynamical
pressure in the disk midplane.  Figure \ref{fig:colortrend} assess this
directly by plotting the error-weighted mean trend in $\sigma_a/v_{{\rm
H}\alpha}$ for the quartiles of the $N-r$ distribution of the
asymmetric-drift sample.  The error bars represent the error-weighted
standard deviation of the data in each bin, whereas the error-weighted
standard error is always smaller than the plotted point.  There is a
marginal detection of a slightly larger $\sigma_a/v_{{\rm H}\alpha}$ in
the reddest bin; however, more data would be required to lend this
result any statistical significance.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%
\begin{center}
%
\includegraphics[width=1.0\columnwidth]{figs/adov_vs_color.pdf}
%
\end{center}
%
\caption{
%
The error-weighted mean trend in $\sigma_a/v_{{\rm H}\alpha}$ binned in
quartiles of the global $N-r$ color (black points).  The error bars
represent the error-weighted standard deviation of the data within each
bin; the error-weighted standard error is smaller than the size of each
black point.  The underlying gray histogram provides the number of
measurements in bins of $N-r$; each quartile contains $\sim$152
galaxies.
%
}
%
\label{fig:colortrend}
%
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
\label{sec:discussion}

\subsection{Technical Concerns}

[[Sample bias]]

[[Beam-smearing]]

\subsection{Prospects}

If $\sigma_a$ is a direct proxy for $\sigma_R$ ...

\bibliography{../master}

\end{document}

% Under the nominal assumptions of (i) a radially independent rotation
% speed and SVE shape and (ii) a exponential dispersion profile with an
% e-folding length of twice the disk scale length ($h_R$, ref), equation
% \ref{eq:adformal} can be used to show asymmetric drift will be maximum
% at 1.25$h_R$, or approximately 0.7$R_{\rm eff}$.

%\begin{deluxetable*}{ r r r r r r r r }
%\tabletypesize{\small}
%\tablewidth{0pt}
%\tablecaption{Linear Regressions for $M_i$ [[Check slope-intercept form]]}
%\tablehead{ \colhead{Dependent} & \multicolumn{3}{c}{Parametric Form} && \multicolumn{3}{c}{Slope-intercept Form} \\
%    \cline{2-4} \cline{6-8}
%    \colhead{Variable} & \colhead{$y_0$} & \colhead{$\phi$} & \colhead{$\varepsilon$} 
%                        && \colhead{$m$} & \colhead{$b$} & \colhead{$\varepsilon_y$} }
%\startdata
% $v_{{\rm H}\alpha}$                &      2.168 &    170.70 &      0.069 &&     -0.164 &     -1.20 &      0.070 \\
%                                    & $\pm$0.003 & $\pm$0.15 & $\pm$0.001 && $\pm$0.003 & $\pm$0.05 & $\pm$0.001 \\[2pt]
% $\log(\sigma_a^2)$                 &       3.78 &     160.1 &      0.209 &&     -0.362 &     -3.69 &      0.222 \\
%                                    &  $\pm$0.01 &  $\pm$0.5 & $\pm$0.005 && $\pm$0.009 & $\pm$0.19 & $\pm$0.005 \\[2pt]
% $\log(\sigma_a/v_{{\rm H}\alpha})$ &     -0.269 &     -0.24 &      0.068 &&     -0.004 &     -0.36 &      0.068 \\
%                                    & $\pm$0.003 & $\pm$0.17 & $\pm$0.002 && $\pm$0.003 & $\pm$0.06 & $\pm$0.002
%\enddata
%\label{tab:lines}
%\end{deluxetable*}

### 2017-02-16 ms.tex
added massive bibtex repo

@@
 
-\input{../dm_nomenclature/dmnom_rv4.tex}
+%\input{../dm_nomenclature/dmnom_rv4.tex}
 
@@
 (ii) differences in the measured H$\alpha$ and stellar systemic velocity
-of less than 20 \kms, (iii) dynamical centers that are consistent to
+of less than 20 km/s, (iii) dynamical centers that are consistent to
 within a fiber diameter of the morphological center [[check]], (iv)
@@
 
-\bibliography{../master}
+\bibliography{master}
 

### 2017-08-02 ms.tex
fixed column header
01 Aug mods

@@
 %       05 Feb 2017: (KBW) v01: stab in the dark
+%       01 Aug 2017: (KBW) edits and summary of todo tasks
 %
@@
 \usepackage{graphicx}
+\usepackage{color}
 \bibliographystyle{apj}
@@
 \slugcomment{Draft: 14 Feb 2017}
+
+% Some fancy commenting
+\definecolor{todo}{RGB}{200,0,0}
+\newcommand{\comment}[2][todo]{{\color{#1}[[{\bf #2}]]}}
+
+\newcommand{\kms}{{km$~\!$s$^{-1}$}}
+\newcommand{\nsaz}{$z_{\rm NSA}$}
+\newcommand{\halpha}{H$\alpha$}
 
@@
 
-Using the statistical prowess of the SDSS-IV/MaNGA survey, we
-demonstrate a strong trend between the strength of lag of the stellar
-rotation curve behind that of the ionized gas as a function of its
-absolute luminosity.
+Asymmetric drift (AD) is the lag of the mean rotation velocity of the
+stellar disk behind the circular speed defined by the total
+gravitational potential.  Although it is often considered a nuisance
+correction one must apply in circular-speed calculations, the direct
+connection between AD and the stellar phase-space distribution function
+makes it an interesting dynamical properties of galaxies in and of
+itself.  The SDSS-IV/MaNGA survey provides more than an order of
+magnitude increase in any galaxy sample size useful for AD measurements.
+In this pilot Letter, we study the empirical correlation between AD, or
+more precisely the differential tangential lag between the stellar
+component and \halpha-emitting gas, and global photometric properties
+from the NASA-Sloan Atlas.  We isolate a set of galaxies with \halpha\
+and stellar velocity fields that are well-fit by simple disk models.
+Our sample of $\sim$800 galaxies shows a clear correlation between
+absolute $i$-band magnitude and AD measured at half an effective radius.
+Removing the primary dependence on the rotation speed, we find that the
+stellar disk rotation is 90\% of the \halpha\ rotation speed, in the
+mean.  Our sample size allows us to infer a weak, yet statistically
+significant, trend with galaxy $N-r$ color such that, in the mean,
+redder galaxies have moderately larger AD relative to their rotation
+speeds.  Within the context of an albeit strong set of assumptions,
+including a direct proportionality between AD and stellar velocity
+dispersion as seen in the Milky Way, we argue that our results suggest
+little variation in the mean disk mass-to-light ratio as a function of
+absolute magnitude and only modest variations with galaxy color
+\comment{last sentence TBD; is Figure 3 consistent with SPS
+variations?}.
 
@@
 
-Asymmetric drift is the lag of the ensemble stellar rotation speed
-behind the circular speed defined by the gravitational potential.  For
-stellar ensembles, \citet[][Section 4.4.3]{2008gady.book.....B} provide
-an intuitive description of asymmetric drift as arising due to the
-combined effect of the radially decreasing surface-density and
-velocity-dispersion profiles typical of axisymmetric systems.  Using the
-$v_R$ moment of the collisionless Boltzmann equation, one obtains the
-Jeans (ref) equation that directly relates the circular speed ($v_c$),
-the mean stellar tangential speed ($\overline{v_\theta}$), and the
-stellar velocity ellipsoid (SVE) as a function of radius in the plane of
+For ensembles of stars in a galaxy disk, \citet[][Section
+4.4.3]{2008gady.book.....B} provide an intuitive description of
+asymmetric drift (AD) as arising due to the combined effect of the
+radially decreasing surface-density and velocity-dispersion profiles
+typical of axisymmetric systems.  Using the $v_R$ moment of the
+collisionless Boltzmann equation, one obtains the Jeans \comment{ref}
+equation that directly relates the circular speed ($v_c$), the mean
+stellar tangential speed ($\overline{v_\theta}$), and the stellar
+velocity ellipsoid (SVE) as a function of radius in the plane of
 symmetry:
@@
 covariance between the radial and vertical motions as a function of
-perpendicular distance to the plane of symmetry --- is negligible (cf.
-Cuddeford \& Amendt).
+perpendicular distance to the plane of symmetry --- is negligible
+\comment{cf.  Cuddeford \& Amendt}.
 
 Asymmetric drift has been measured in numerous systems.  Perhaps most
-notably, e.g., Dehnen \& Binney have shown that populations of stars
-show a direct correlation between their velocity dispersion and the
-degree to which their mean rotation speed lags behind that of the Local
-Standard of Rest (LSR), much in line with the expectation provided by
-equation \ref{eq:adformal}.  Although there have been some studies of
-asymmetric drift in external galaxies (refs), it is often treated as a
+notably, e.g., \comment{Dehnen \& Binney} have shown that populations of
+stars show a direct correlation between their velocity dispersion and
+the degree to which their mean rotation speed lags behind that of the
+Local Standard of Rest (LSR), much in line with the expectation provided
+by equation \ref{eq:adformal}.  Although there have been some studies of
+AD in external galaxies \comment{refs}, it is often treated as a
 nuisance phenomenon that must be corrected for when trying to constrain
-the circular speed curve of a galaxy (refs).  The ubiquity and
-phenomenology of asymmetric drift as a salient observable has not yet
-been studied for a statistically significant population of galaxies.
-Our aim is therefore to provide a first look at the correlation between
-asymmetric drift measurements and basic broad-band photometric
-properties for a large sample of galaxies.
+the circular speed curve of a galaxy \comment{refs}.  The ubiquity and
+phenomenology of AD as a salient observable has not yet been studied for
+a statistically significant population of galaxies.  Our aim is
+therefore to provide a first look at the correlation between AD
+measurements and basic broad-band photometric properties for a large
+sample of galaxies.
 
@@
 %
-\includegraphics[width=0.8\textwidth]{figs/cmd_flux.pdf}
+\includegraphics[width=0.9\textwidth]{figs/cmd_flux.pdf}
 %
@@
 the subsample of galaxies {\em not} selected to be kinematically regular
-(middle; see text), and the asymmetric-drift sample used throughout the
-remainder of our analysis.  The color of the data points in the top row
-represent the mean H$\alpha$ surface brightness [[check aperture]]
-according to the colorbar to the right; the bottom row replaces the
-color by the $r$-band surface brightness density.
+(middle; see text), and the AD sample used throughout the remainder of
+our analysis.  The color of the data points in the top row represent the
+mean \halpha\ surface brightness \comment{check aperture} according to
+the colorbar to the right; the bottom row replaces the color by the
+$r$-band surface brightness density.
 %
@@
 In addition to the basic understanding of this dynamically relevant
-quantity, our interest in asymmetric drift stems from its fundamental
-dynamical connection to the full phase-space distribution function of a
-galaxy's stars, as empirically demonstrated in the Milky Way.  Indeed,
-Westfall et al. (2011) (see also refs) used asymmetric drift to
-constrain the axial ratios of the SVE given direct measurements of the
-line-of-sight (LOS) stellar velocity dispersion, $\sigma$.
-Alternatively, if one can statistically constrain the shape of the SVE
-(refs), measurements of asymmetric drift could be used as a proxy for
-stellar $\sigma$ by either appealing to equation \ref{eq:adformal} or an
-empirical relation calibrated by samples with both asymmetric drift and
-$\sigma$ measurements.  Such a use of asymmetric drift as a proxy for
-stellar $\sigma$ is attractive in the low-surface-brightness and
-low-velocity-dispersion regimes where direct measurements are difficult
-and/or expensive.  We commit to this paradigm by using the following
-nomenclature for asymmetric drift, following from equation
-\ref{eq:adformal}:
+quantity, our interest in AD stems from its fundamental dynamical
+connection to the full phase-space distribution function of a galaxy's
+stars, as empirically demonstrated in the Milky Way.  Indeed,
+\comment{Westfall et al. (2011; see also refs} used AD to constrain the
+axial ratios of the SVE given direct measurements of the line-of-sight
+(LOS) stellar velocity dispersion, $\sigma$.  Alternatively, if one can
+statistically constrain the shape of the SVE \comment{refs},
+measurements of AD could be used as a proxy for stellar $\sigma$ by
+either appealing to equation \ref{eq:adformal} or an empirical relation
+calibrated by samples with both AD and $\sigma$ measurements \comment{in
+prep...}.  Such a use of AD as a proxy for stellar $\sigma$ is
+attractive in the low-surface-brightness and low-velocity-dispersion
+regimes where direct measurements are difficult and/or expensive.  We
+commit to this paradigm by using the following nomenclature for AD,
+following from equation \ref{eq:adformal}:
 %
@@
 For disk galaxies, there is a decades-long industry of using cold-gas
-tracers to construct circular-speed curves of galaxies (refs).  These
-data have provided the first concrete arguments for the presence of
-massive dark-matter halos (ref) based on mass model reconstruction
-(refs) and have formed the basis for the most robust Tully-Fisher
-relations compiled for the local Universe (refs).  However, it is
-important to acknowledge that one cannot directly measure $v_c$,
-effectively making $\sigma_a$ unobservable.  That is, every dynamical
-tracer has some non-zero dynamical pressure such that it will lag behind
-the theoretically defined circular speed.  There are very clear examples
-of early-type galaxies that show differential asymmetric-drift in their
-molecular (e.g., CO), atomic (e.g., \ion{H}{1}), and/or ionized
-(H$\alpha$) tracers relative to a robust mass model of $v_c$ (Davis et
-al.) due to the different turbulent/thermal pressures intrinsic to these
-tracers.  However, these signatures are much less apparent in disk
-galaxies.  For example, Martinsson et al.\ show that H$\alpha$ and
-\ion{H}{1} rotation curves are consistent for the DiskMass Survey within
-the limits of their constraints on beam-smearing, suggesting that any
-correction for the lag of either behind the circular speed should be
-small.  Indeed, theoretical calculations (Dalcanton \& Stilp) suggest
-that gas-pressure corrections to \ion{H}{1} rotation curves should be
-largely negligible for galaxies with ${\mathcal M} > 10^x {\mathcal
-M}_\odot$.  Nevertheless, we emphasize here that our measurements of
+tracers to construct circular-speed curves of galaxies \comment{refs}.
+These data have provided the first concrete arguments for the presence
+of massive dark-matter halos \comment{ref} based on mass-model
+reconstruction \comment{refs} and have formed the basis for the most
+robust Tully-Fisher relations compiled for the local Universe
+\comment{refs}.  However, it is important to acknowledge that one cannot
+directly measure $v_c$, effectively making $\sigma_a$ unobservable.
+That is, every dynamical tracer has some non-zero dynamical pressure
+such that it will lag behind the theoretically defined circular speed.
+There are very clear examples of early-type galaxies that show
+differential AD in their molecular (e.g., CO), atomic (e.g.,
+\ion{H}{1}), and/or ionized (\halpha) tracers relative to a robust mass
+model of $v_c$ \comment{Davis et al.}, due to the different
+turbulent/thermal pressures intrinsic to these tracers.  However, these
+signatures are much less apparent in disk galaxies.  For example,
+\comment{Martinsson et al.} show that \halpha\ and \ion{H}{1} rotation
+curves are consistent for the DiskMass Survey within the limits of their
+constraints on beam-smearing, suggesting that any correction for the lag
+of either behind the circular speed should be small.  Indeed,
+theoretical calculations \comment{Dalcanton \& Stilp} suggest that
+gas-pressure corrections to \ion{H}{1} rotation curves should be largely
+negligible for galaxies with \comment{${\mathcal M} > 10^x {\mathcal
+M}_\odot$}.  Nevertheless, we emphasize here that our measurements of
 $\sigma_a$ may be better termed as a {\em differential tangential lag}
 because they are based on the quadrature difference between the observed
-H$\alpha$ and stellar rotation curves in our galaxy sample (Section
+\halpha\ and stellar rotation curves in our galaxy sample (Section
 \ref{sec:data}).  These measurements are perfectly valid in their own
 right; however, it is their interpretation in the context of the
-theoretical definition of asymmetric drift that should be questioned in
-some regimes, as discussed in Section \ref{sec:discussion}.
+theoretical definition of AD that should be questioned in some regimes,
+as discussed in Section \ref{sec:discussion}.
 
@@
 correlation between the absolute $i$-band magnitude of a galaxies and
-the strength of its asymmetric drift measured at half of an effective
-radius (0.5 $R_{\rm eff}$).  We also illustrate the weak color
-dependence in this relation.  We summarize and discuss these results in
-Section \ref{sec:discussion}.
+the strength of its AD measured at half of an effective radius (0.5
+$R_{\rm eff}$).  We also illustrate the weak color dependence in this
+relation.  We summarize and discuss these results in Section
+\ref{sec:discussion}. \comment{flesh out}
 
@@
 observations.  The kinematic measurements are provided by the MaNGA data
-analysis pipeline (DAP; Westfall et al., in prep): the ionized-gas
-kinematics are based on simple single-Gaussian fits to the H$\alpha$
-emission feature and the stellar kinematics are determined using pPXF
-(Cappellari et al.) with the MILES stellar template library (Jesus FB et
-al.).
+analysis pipeline \comment{DAP; Westfall et al., in prep}: the
+ionized-gas kinematics are based on simple single-Gaussian fits to the
+\halpha\ emission feature and the stellar kinematics are determined
+using {\tt pPXF} (Cappellari et al.) with the MILES stellar template
+library \comment{Jesus FB et al.}.
 
-The MaNGA galaxy selection (Wake et al. in prep) is a simple cut in
+The MaNGA galaxy selection \comment{Wake et al} is a simple cut in
 absolute $i$-band magnitude, $M_i$, and redshift, $z$, and provides a
-complete sampling of the overall galaxy population.  As such,
-measurements of stellar and/or H$\alpha$ rotation curves for some
+complete \comment{check} sampling of the overall galaxy population.  As
+such, measurements of stellar and/or \halpha\ rotation curves for some
 systems will be difficult/impossible.  Using the photometry from the
-NASA-Sloan Atlas (ref),\footnote{\url{nsatlas.org}} Figure
+NASA-Sloan Atlas \comment{ref},\footnote{\url{nsatlas.org}} Figure
 \ref{fig:sample} shows the color-magnitude diagram of all galaxies
-colored by their mean H$\alpha$ and $r$-band surface brightness.
-[[TODO: Need to check this plot.]] Although not excluded from our
-velocity-field analysis {\em a priori}, we expect to obtain poor
-rotation curve measurements for galaxies with low H$\alpha$ and stellar
-surface brightness.\footnote{
+colored by their mean \halpha\ and $r$-band surface brightness.
+\comment{ Check the details of how this plot was constructed}  Although
+not excluded from our velocity-field analysis {\em a priori}, we expect
+to obtain poor rotation-curve measurements for galaxies with low
+\halpha\ and stellar surface brightness.\footnote{
 %
-The uniformity of the MaNGA survey (Law et al. 2015) is such that S/N is
-tightly correlated with surface brightness.}
+The uniformity of the MaNGA survey \comment{Law et al. 2015} is such
+that the signal-to-noise (S/N) of the datacube spaxels is tightly
+correlated with surface brightness.}
 
-[[Extinction corrections for the CMD?]]
+\comment{Extinction corrections for the CMD?}
 
 We model the geometric projection of the rotational plane of each galaxy
-using the approach presented by Andersen \& Bershady (2013); see also
-Westfall et al. (2011).  In three independent fitting iterations, the
-model fits are optimized for the H$\alpha$ velocity field, the stellar
-velocity field, and simultaneously for both data sets; for the latter,
-the geometry is forced to be the same for the two dynamical tracers, but
-the parametrized rotation curves are independent.  We use these
-velocity-field-fitting results to objectively isolate a set of
-``kinematically regular'' galaxies.  Briefly, galaxies in this sample
+using the approach presented by \comment{Andersen \& Bershady (2013)};
+see also \comment{Westfall et al. (2011)}.  In three independent fitting
+iterations, the model fits are optimized for the \halpha\ velocity
+field, the stellar velocity field, and simultaneously for both data
+sets; for the latter, the geometry is forced to be the same for the two
+dynamical tracers, but the parametrized rotation curves are independent.
+We use these velocity-field-fitting results to objectively isolate a set
+of ``kinematically regular'' galaxies.  Briefly, galaxies in this sample
 must have: (i) successful velocity-field fits for all three approaches,
-(ii) differences in the measured H$\alpha$ and stellar systemic velocity
+(ii) differences in the measured \halpha\ and stellar systemic velocity
 of less than 20 km/s, (iii) dynamical centers that are consistent to
-within a fiber diameter of the morphological center [[check]], (iv)
-H$\alpha$ and stellar velocity-field position angles that are consistent
-to within $\pm$15$\arcdeg$, and (v) kinematic inclinations between
-$15\arcdeg < i < 80\arcdeg$ that are both consistent between the
-H$\alpha$ and stellar data and with respect to the photometric
-ellipticity to within $\pm$20$\arcdeg$.  The constraint on the
-inclination is by far the most stringent. [[give number of galaxies cut
-by each criterion?]]  Applying these constraints yields a sample of 798
-observations (for 790 unique galaxies) out of the 2764 observations
-analyzed.  Eleven galaxies with repeat observations satisfy the
-selection criteria; however, only five of these show all observations
-are consistently selected, whereas the other six show one or more of the
-observations did not pass our constraints [[we should understand
-this.]].  [[TBD: Finally, we also visually inspected the broad-band
-imaging of these 790 galaxies and eliminated merging and highly
-extincted (highly inclined) systems yielding a final sample of XXX
-galaxies.]]  We hereafter refer to galaxies that satisfy our selection
-criteria as the ``asymmetric-drift'' sample.
+within a fiber diameter of the morphological center \comment{check the
+details of this}, (iv) \halpha\ and stellar velocity-field position
+angles that are consistent to within $\pm$15$\arcdeg$, and (v) kinematic
+inclinations between $15\arcdeg < i < 80\arcdeg$ that are both
+consistent between the \halpha\ and stellar data and with respect to the
+photometric ellipticity to within $\pm$20$\arcdeg$.  The constraint on
+the inclination is by far the most stringent. \comment{give number of
+galaxies cut by each criterion?}  Applying these constraints yields a
+sample of 798 observations (for 790 unique galaxies) out of the 2764
+observations analyzed.  Eleven galaxies with repeat observations satisfy
+the selection criteria; however, only five of these show all
+observations are consistently selected, whereas the other six show one
+or more of the observations did not pass our constraints \comment{we
+should understand why repeat observations are not consistent for the
+majority of cases.  low S/N?}.  \comment{Do this or remove the
+sentence:} Finally, we also visually inspected the broad-band imaging of
+these 790 galaxies and eliminated merging and highly extincted (highly
+inclined) systems yielding a final sample of XXX galaxies.  We hereafter
+refer to galaxies that satisfy our selection criteria as the ``AD
+sample''.
 
@@
 MaNGA galaxies, as well as the distributions of those galaxies included
-and excluded from our asymmetric-drift sample.  As expected, galaxies
-with relatively high H$\alpha$ and $r$-band surface brightness are
-preferentially selected, excluding much of the red sequence as well as
-the brightest and faintest galaxies in the blue cloud.  Although the
-conclusions we reach based on our asymmetric drift sample are
-astrophysically meaningful, it is important to appreciate the biased
-representation of the overall galaxy population represented by the
-sample in our analysis.  [[Show histogram of kinematically regular
-sample against the volume-corrected distribution of the MaNGA parent
-sample in Mi and N-r, and discuss.]]
+and excluded from our AD sample.  As expected, galaxies with relatively
+high \halpha\ and $r$-band surface brightness are preferentially
+selected.  This results in an exclusion of much of the red sequence, as
+well as the brightest and faintest galaxies in the blue cloud.  Although
+the conclusions we reach based on our AD sample are astrophysically
+meaningful, it is important to appreciate that the galaxies in our AD
+sample are a biased representation of the overall galaxy population.
+
+\comment{Show histogram of kinematically regular sample against the
+volume-corrected distribution of the MaNGA parent sample in Mi and N-r,
+and discuss.}
 
 Our velocity-fitting method provides a model rotation curve fit to both
-the H$\alpha$ and stellar data, each parametrized as a hyperbolic
-tangent function: $v_{\rm rot} = v_{\rm flat} \tanh(R/h_v)$.  However,
-our primary result is based on the error-weighted mean of the
-deprojected rotation curve measurements for each dynamical tracer within
-$\pm$30$\arcdeg$ of the major axis and $2\farcs5$ radial bins centered
-at 0.25, 0.5, 0.75, 1.0, and 1.25 $R_{\rm eff}$ --- $R_{\rm eff}$ is the
-effective radius using the elliptical Petrosian analysis from the
-NASA-Sloan Atlas. [[Check that $R_{\rm eff}$ includes the multiplicative
-offset to match these Petrosian and Sersic $R_{\rm eff}$ in the mean.]]
-Specifically, we calculate the error-weighted mean and standard
-deviation of $v_j = V_j/\cos\theta_j/\sin i$ and
+the \halpha\ and stellar data, each parametrized as a hyperbolic tangent
+function: $v_{\rm rot} = v_{\rm flat} \tanh(R/h_v)$.  However, our
+primary result is based on the error-weighted mean of the deprojected
+rotation-curve measurements for each dynamical tracer.  We only include
+measurements within $\pm$30$\arcdeg$ of the major axis and construct
+radial bins that are $2\farcs5$ wide and centered at 0.25, 0.5, 0.75,
+1.0, and 1.25 $R_{\rm eff}$ --- $R_{\rm eff}$ is the effective radius
+using the elliptical Petrosian analysis from the NASA-Sloan Atlas.
+\comment{Check if the $R_{\rm eff}$ does or does not include the
+multiplicative offset to match these Petrosian and Sersic $R_{\rm eff}$
+in the mean.}  Specifically, we calculate the error-weighted mean and
+standard deviation of $v_j = V_j/\cos\theta_j/\sin i$ and
 %
@@
 
-[[An example demonstrating the details of our measurements is
-illustrated in Figure X.]]
+\comment{An example demonstrating the details of our measurements is
+illustrated in Figure X.}
 
@@
 quadrature sum of the error-weighted standard error (i.e., the
-error-weighted standard deviation divided by $\sqrt N$) and the
-propagated error in the error-weighted mean. [[Can revisit this.
-Details of error calculation not all that important.  We're dominated by
-intrinsic deviations from the regression.]]
+error-weighted standard deviation divided by $\sqrt{N}$) and the
+propagated error in the error-weighted mean. \comment{Should we revisit
+this?  Details of error calculation not all that important.  We're
+dominated by intrinsic deviations in the regressions below.}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 %
-Global photometry measurements versus kinematics measurements at
-$R=R_{\rm eff}$ for the asymmetric-drift sample: $M_i$ versus (a) $N-r$
-color with each point colored according to $\sigma_a^2$, (b) $v_{{\rm
-H}\alpha}$ with each point colored according to $\sigma_a^2$, (c)
-$\sigma_a^2$ with each point colored according to $v_{{\rm H}\alpha}$,
-and (d) $\sigma_a/v_{{\rm H}\alpha}$ with each point colored by the
-$N-r$ color.  Panels (b), (c), and (d) include the Spearman rank
-correlation coefficient, $r_s$, and the linear regressions (solid lines)
-constructed from the median parameters provided in Table
-\ref{tab:lines}.  The dashed lines are offset from linear regression by
-the modeled intrinsic scatter in the relation ($\varepsilon_y$).
+Global photometry and kinematic measurements at $R=R_{\rm eff}/2$ for
+the AD sample: $M_i$ versus (a) $N-r$ color with each point colored
+according to $\sigma_a^2$, (b) $v_{{\rm H}\alpha}$ with each point
+colored according to $\sigma_a^2$, (c) $\sigma_a^2$ with each point
+colored according to $v_{{\rm H}\alpha}$, and (d) $\sigma_a/v_{{\rm
+H}\alpha}$ with each point colored by the $N-r$ color.  Panels (b), (c),
+and (d) include the Spearman rank correlation coefficient, $r_s$, and
+the linear regressions (solid lines) constructed from the parameters
+provided in Table \ref{tab:lines}.  The dashed lines are offset from
+linear regression by the modeled intrinsic scatter in the relation
+($\varepsilon_y$).
 %
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \ref{fig:correlation}(c), and \ref{fig:correlation}(d), respectively.
-The points are colored according to the color bar and quantity to the
-right of each panel.  Each panel provides the Spearman rank correlation
-coefficient, $r_s$, of the plotted data with errors derived from $10^3$
-bootstrap simulations.  We have also used a Markov Chain Monte Carlo
-(refs) to sample the Bayesian posterior distribution for a linear
-regression to the data in each panel, incorporating the errors in both
-axes (refs); the errors in the kinematic quantities are always dominant.
-The fitted model is a line in parametric form with an intrinsic Gaussian
-scatter perpendicular to the line.  That is, the line is defined as
-$\mathbf{l}(t) = \mathbf{l}_0 + t\ \hat{\mathbf{l}}$ for a generalized
-coordinate $t$ along the line, an origin $\mathbf{l}_0 = \{x_0, y_0\}$,
-and the unit vector $\hat{\mathbf{l}} = \{\cos\phi, \sin\phi\}$.  The
-fitted parameters are $y_0$, $\phi$, and the dispersion of the intrinsic
-Gaussian scatter about the line, $\varepsilon$; $x_0$ is fixed at the
-median abscissa of the data being fitted ($x_0 = M_{i,0} = -20.6$).
-Uniform priors are used for $y_0$ and $\phi$ and a logarithmic prior
-[[check]] is used for $\varepsilon$ (ref).  Using the returned samples
-of the posterior, we also provide parameters for the slope-intercept
-form of the line --- $y = mx + b$ where $m = \tan\phi$ and $b = y_0 -
-x_0 \tan\phi$ --- and the scatter projected along the ordinate,
-$\varepsilon_y = \varepsilon/|\cos\phi$|.  Table \ref{tab:lines}
-provides the median and standard deviation of the marginalized
-distribution of each parameter; these parameters have been used to
-construct the lines provided in Figure \ref{fig:correlation}.
+The points are colored according to the label to the right of each color
+bar.  Each panel provides the Spearman rank-correlation coefficient,
+$r_s$, of the plotted data with errors derived from $10^3$ bootstrap
+simulations.  We have also used a Markov Chain Monte Carlo
+\comment{refs} to sample the Bayesian posterior distribution for a
+linear regression to the data in each panel, incorporating the errors in
+both axes \comment{refs}; the errors in the kinematic quantities always
+dominate over the absolute magnitude errors.  The fitted model is a line
+in parametric form with an intrinsic Gaussian scatter perpendicular to
+the line.  That is, the line is defined as $\mathbf{l}(t) = \mathbf{l}_0
++ t\ \hat{\mathbf{l}}$ for a generalized coordinate $t$ along the line,
+an origin $\mathbf{l}_0 = \{x_0, y_0\}$, and the unit vector
+$\hat{\mathbf{l}} = \{\cos\phi, \sin\phi\}$.  The fitted parameters are
+$y_0$, $\phi$, and the dispersion of the intrinsic Gaussian scatter
+about the line, $\varepsilon$; $x_0$ is fixed at the median abscissa of
+the data being fitted ($x_0 = M_{i,0} = -20.6$).  Uniform priors are
+used for $y_0$ and $\phi$ and a logarithmic prior \comment{check this is
+true} is used for $\varepsilon$ \comment{ref}.  Using the returned
+samples of the posterior, we also provide parameters for the
+slope-intercept form of the line --- $y = mx + b$ where $m = \tan\phi$
+and $b = y_0 - x_0 \tan\phi$ --- and the scatter projected along the
+ordinate, $\varepsilon_y = \varepsilon/|\cos\phi$|.  Table
+\ref{tab:lines} provides the median and standard deviation of the
+marginalized distribution of each parameter; these parameters have been
+used to construct the lines provided in Figure \ref{fig:correlation}.
 
@@
 \tablewidth{0pt}
-\tablecaption{Linear Regressions for $M_i$
-    [[Check slope-intercept form]]}
-\tablehead{ & \multicolumn{3}{c}{Dependent Variable} \\
-    \cline{2-4} \\[-3pt]
- \colhead{Parameter} & \colhead{$v_{{\rm H}\alpha}$} &
+\tablecaption{Linear Regressions for $M_i$ \comment{check m-b form}}
+\tablehead{ & \multicolumn{3}{c}{Dependent Variable} \\ \cline{2-4} \\[-3pt]
+ \colhead{Parameter} & \colhead{$\log(v_{{\rm H}\alpha})$} &
  \colhead{$\log(\sigma_a^2)$} &
@@
 and $M_i$.  However, it is important to note that Figure
-\ref{fig:correlation}(b) does not present the Tully-Fisher (ref)
-relation for our asymmetric-drift sample; the Figure gives the rotation
-speed at $R=0.5R_{\rm eff}$, not a measure of the full-width of the
-dynamically broadened line profile.  The slope of the relation in Figure
+\ref{fig:correlation}(b) does not present the Tully-Fisher \comment{ref}
+relation for our AD sample; the Figure gives the rotation speed at
+$R=0.5R_{\rm eff}$, not a measure of the full-width of the dynamically
+broadened line profile.  The slope of the relation in Figure
 \ref{fig:correlation}(b) is steeper than a nominal Tully-Fisher relation
 because galaxies at low luminosity tend to have more slowly rising
-rotation curves (refs), which can be confirmed by plotting $h_{v,{\rm
-H}\alpha}/R_{\rm eff}$ as a function of $M_i$. [[actually show this?]]
+rotation curves \comment{refs}, which can be confirmed by plotting
+$h_{v,{\rm H}\alpha}/R_{\rm eff}$ as a function of $M_i$.
+\comment{actually show this?}
 
@@
 $v_{\ast} \sim 0.9 v_{{\rm H}\alpha}$.  Although the radius at which the
-asymmetric drift was sampled is different, this ratio is consistent with
-galaxies from the DiskMass survey (Martinsson et al.).
+AD was sampled is different, this ratio is consistent with a similar
+ratio measured for DiskMass-Survey galaxies \comment{Martinsson et al.}.
 
@@
 H}\alpha}$ and global galaxy color.  One might expect such a correlation
-if, for example, galaxies with different global color different
-light-weightings of the thin vs. thick-disk (refs [[not sure there are
-relevant ones]]), which propagates to a different dominant dynamical
-pressure in the disk midplane.  Figure \ref{fig:colortrend} assess this
-directly by plotting the error-weighted mean trend in $\sigma_a/v_{{\rm
-H}\alpha}$ for the quartiles of the $N-r$ distribution of the
-asymmetric-drift sample.  The error bars represent the error-weighted
-standard deviation of the data in each bin, whereas the error-weighted
-standard error is always smaller than the plotted point.  There is a
-marginal detection of a slightly larger $\sigma_a/v_{{\rm H}\alpha}$ in
-the reddest bin; however, more data would be required to lend this
-result any statistical significance.
+if, for example, galaxies with different global color have different
+light-weightings of the thin vs. thick-disk \comment{refs; not sure
+there are relevant ones; Comer\'{o}n?}, which propagates to a difference
+in which component dominates the dynamical pressure in the disk
+midplane.  Figure \ref{fig:colortrend} assesses this directly by
+plotting the error-weighted mean trend in $\sigma_a/v_{{\rm H}\alpha}$
+for quartiles of the $N-r$ distribution of the AD sample.  The error
+bars represent the error-weighted standard deviation of the data in each
+bin, whereas the error-weighted standard error is always {\it smaller
+than the plotted point}.  This suggests a marginal, yet statistically
+significant, detection of a slightly larger $\sigma_a/v_{{\rm H}\alpha}$
+in the reddest bin.
+
+%; however, more data would be required to lend this result any
+%statistical significance.
 
@@
 
-[[Sample bias]]
+\comment{Sample bias}
 
-[[Beam-smearing]]
+\comment{Beam-smearing}
 
@@
 
-If $\sigma_a$ is a direct proxy for $\sigma_R$ ...
+\comment{If $\sigma_a$ is a direct proxy for $\sigma_R$ ...}
 

### 2017-12-13 ms.tex
test
reference edits

@@
 
+% Project collaborators: Matthew Bershady, Anne-Marie Weijmans, Karen
+% Masters, Michael Merrifield, Jo Bovy, Kevin Bundy, Niv Drory, Thomas
+% Martinsson, Joel Brownstein, Daniel Thomas, Dmitry Bizyaev, David Law,
+% Andres Meza, Aaron A. Dutton
+
 \begin{abstract}
@@
 magnitude increase in any galaxy sample size useful for AD measurements.
-In this pilot Letter, we study the empirical correlation between AD, or
-more precisely the differential tangential lag between the stellar
-component and \halpha-emitting gas, and global photometric properties
-from the NASA-Sloan Atlas.  We isolate a set of galaxies with \halpha\
-and stellar velocity fields that are well-fit by simple disk models.
-Our sample of $\sim$800 galaxies shows a clear correlation between
-absolute $i$-band magnitude and AD measured at half an effective radius.
-Removing the primary dependence on the rotation speed, we find that the
-stellar disk rotation is 90\% of the \halpha\ rotation speed, in the
-mean.  Our sample size allows us to infer a weak, yet statistically
-significant, trend with galaxy $N-r$ color such that, in the mean,
-redder galaxies have moderately larger AD relative to their rotation
-speeds.  Within the context of an albeit strong set of assumptions,
-including a direct proportionality between AD and stellar velocity
-dispersion as seen in the Milky Way, we argue that our results suggest
-little variation in the mean disk mass-to-light ratio as a function of
-absolute magnitude and only modest variations with galaxy color
-\comment{last sentence TBD; is Figure 3 consistent with SPS
+In this pilot study, we demonstrate the empirical correlation between
+AD, or more precisely the differential tangential lag between the
+stellar component and \halpha-emitting gas, and global photometric
+properties from the NASA-Sloan Atlas.  We isolate a set of galaxies with
+\halpha\ and stellar velocity fields that are well-fit by simple disk
+models.  Our sample of $\sim$800 galaxies shows a clear correlation
+between absolute $i$-band magnitude and AD measured at half an effective
+radius.  Removing the primary dependence on the rotation speed, we find
+that the stellar disk rotation is 90\% of the \halpha\ rotation speed,
+in the mean.  Our sample size allows us to infer a weak, yet
+statistically significant, trend with galaxy $N-r$ color such that, in
+the mean, redder galaxies have moderately larger AD relative to their
+rotation speeds.  Within the context of an albeit strong set of
+assumptions, including a direct proportionality between AD and stellar
+velocity dispersion as seen in the Milky Way, we argue that our results
+suggest little variation in the mean disk mass-to-light ratio as a
+function of absolute magnitude and only modest variations with galaxy
+color \comment{last sentence TBD; is Figure 3 consistent with SPS
 variations?}.
@@
 typical of axisymmetric systems.  Using the $v_R$ moment of the
-collisionless Boltzmann equation, one obtains the Jeans \comment{ref}
-equation that directly relates the circular speed ($v_c$), the mean
-stellar tangential speed ($\overline{v_\theta}$), and the stellar
+collisionless Boltzmann equation, one obtains the Jeans equation
+\citep{Jeans1919} that directly relates the circular speed ($v_c$), the
+mean stellar tangential speed ($\overline{v_\theta}$), and the stellar
 velocity ellipsoid (SVE) as a function of radius in the plane of
@@
 perpendicular distance to the plane of symmetry --- is negligible
-\comment{cf.  Cuddeford \& Amendt}.
+\citep{1991ApJ...368...79A}.
 
@@
 nuisance phenomenon that must be corrected for when trying to constrain
-the circular speed curve of a galaxy \comment{refs}.  The ubiquity and
+the circular speed of a galaxy \comment{refs}.  The ubiquity and
 phenomenology of AD as a salient observable has not yet been studied for
@@
 stars, as empirically demonstrated in the Milky Way.  Indeed,
-\comment{Westfall et al. (2011; see also refs} used AD to constrain the
-axial ratios of the SVE given direct measurements of the line-of-sight
-(LOS) stellar velocity dispersion, $\sigma$.  Alternatively, if one can
-statistically constrain the shape of the SVE \comment{refs},
-measurements of AD could be used as a proxy for stellar $\sigma$ by
-either appealing to equation \ref{eq:adformal} or an empirical relation
-calibrated by samples with both AD and $\sigma$ measurements \comment{in
-prep...}.  Such a use of AD as a proxy for stellar $\sigma$ is
-attractive in the low-surface-brightness and low-velocity-dispersion
-regimes where direct measurements are difficult and/or expensive.  We
-commit to this paradigm by using the following nomenclature for AD,
-following from equation \ref{eq:adformal}:
+\citet{2011ApJ...742...18W} used AD to constrain the axial ratios of the
+SVE given direct measurements of the line-of-sight (LOS) stellar
+velocity dispersion, $\sigma$.  Alternatively, if one can leverage
+statistical constraints on the shape of the SVE
+\citep[e.g.][]{2012MNRAS.423.2726G}, measurements of AD can be used as a
+proxy for stellar $\sigma$ via equation \ref{eq:adformal}.  Such a use
+of AD-$\sigma$ relation is attractive in the low-surface-brightness and
+low-velocity-dispersion regimes where direct measurements are difficult
+and/or expensive.  We commit to this paradigm by using the following
+nomenclature for AD, following from equation \ref{eq:adformal}:
 %
@@
 
-We present the data used for our analysis in the following section.  In
-Section \ref{sec:results}, we demonstrate that there is a strong
-correlation between the absolute $i$-band magnitude of a galaxies and
-the strength of its AD measured at half of an effective radius (0.5
-$R_{\rm eff}$).  We also illustrate the weak color dependence in this
-relation.  We summarize and discuss these results in Section
-\ref{sec:discussion}. \comment{flesh out}
+We present the data used for our analysis in the following section.
+Section \ref{sec:results} presents the strong correlation seen in out
+galaxy sample between the absolute $i$-band magnitude and AD signal
+measured at half of an effective radius (0.5 $R_{\rm eff}$).  We also
+illustrate the weak color dependence in this relation.  Finally, we
+summarize and discuss these results in Section \ref{sec:discussion}.
+\comment{flesh out}
 
@@
 using {\tt pPXF} (Cappellari et al.) with the MILES stellar template
-library \comment{Jesus FB et al.}.
+library \comment{Jesus FB et al.}.  \comment{Mention hierarchical
+clustering?}
 
-The MaNGA galaxy selection \comment{Wake et al} is a simple cut in
-absolute $i$-band magnitude, $M_i$, and redshift, $z$, and provides a
-complete \comment{check} sampling of the overall galaxy population.  As
-such, measurements of stellar and/or \halpha\ rotation curves for some
-systems will be difficult/impossible.  Using the photometry from the
-NASA-Sloan Atlas \comment{ref},\footnote{\url{nsatlas.org}} Figure
-\ref{fig:sample} shows the color-magnitude diagram of all galaxies
-colored by their mean \halpha\ and $r$-band surface brightness.
-\comment{ Check the details of how this plot was constructed}  Although
-not excluded from our velocity-field analysis {\em a priori}, we expect
-to obtain poor rotation-curve measurements for galaxies with low
-\halpha\ and stellar surface brightness.\footnote{
+The MaNGA galaxy selection \citep{2017AJ....154...86W} is a simple cut
+in absolute $i$-band magnitude, $M_i$, and redshift, $z$, and provides a
+complete sampling of the overall galaxy population.  As such,
+measurements of stellar and/or \halpha\ rotation curves for some systems
+will be difficult/impossible.  Using the photometry from the NASA-Sloan
+Atlas,\footnote{\url{nsatlas.org}} Figure \ref{fig:sample} shows the
+color-magnitude diagram of all galaxies colored by their mean \halpha\
+and $r$-band surface brightness.  \comment{Update this} Although not
+excluded from our velocity-field analysis {\em a priori}, we expect to
+obtain poor rotation-curve measurements for galaxies with low \halpha\
+and stellar surface brightness.\footnote{
 %
-The uniformity of the MaNGA survey \comment{Law et al. 2015} is such
+The uniformity of the MaNGA survey \citet{2015AJ....150...19L} is such
 that the signal-to-noise (S/N) of the datacube spaxels is tightly
@@
 
+\comment{Primary vs. Secondary sample?}
+
 We model the geometric projection of the rotational plane of each galaxy
-using the approach presented by \comment{Andersen \& Bershady (2013)};
-see also \comment{Westfall et al. (2011)}.  In three independent fitting
-iterations, the model fits are optimized for the \halpha\ velocity
-field, the stellar velocity field, and simultaneously for both data
-sets; for the latter, the geometry is forced to be the same for the two
-dynamical tracers, but the parametrized rotation curves are independent.
-We use these velocity-field-fitting results to objectively isolate a set
-of ``kinematically regular'' galaxies.  Briefly, galaxies in this sample
-must have: (i) successful velocity-field fits for all three approaches,
-(ii) differences in the measured \halpha\ and stellar systemic velocity
-of less than 20 km/s, (iii) dynamical centers that are consistent to
-within a fiber diameter of the morphological center \comment{check the
-details of this}, (iv) \halpha\ and stellar velocity-field position
-angles that are consistent to within $\pm$15$\arcdeg$, and (v) kinematic
-inclinations between $15\arcdeg < i < 80\arcdeg$ that are both
-consistent between the \halpha\ and stellar data and with respect to the
-photometric ellipticity to within $\pm$20$\arcdeg$.  The constraint on
-the inclination is by far the most stringent. \comment{give number of
+using the approach presented by \citep[][see also
+\citealt{2011ApJ...742...18W}]{2003ApJ...599L..79A}.  In three
+independent fitting iterations, the model fits are optimized for the
+\halpha\ velocity field, the stellar velocity field, and simultaneously
+for both data sets; for the latter, the geometry is forced to be the
+same for the two dynamical tracers, but the parametrized rotation curves
+are independent.  We use these velocity-field-fitting results to
+objectively isolate a set of ``kinematically regular'' galaxies.
+Briefly, galaxies in this sample must have: (i) successful
+velocity-field fits for all three approaches, (ii) differences in the
+measured \halpha\ and stellar systemic velocity of less than 20 km/s,
+(iii) dynamical centers that are consistent to within a fiber diameter
+of the morphological center \comment{check the details of this}, (iv)
+\halpha\ and stellar velocity-field position angles that are consistent
+to within $\pm$15$\arcdeg$, and (v) kinematic inclinations between
+$15\arcdeg < i < 80\arcdeg$ that are both consistent between the
+\halpha\ and stellar data and with respect to the photometric
+ellipticity to within $\pm$20$\arcdeg$.  The constraint on the
+inclination is by far the most stringent. \comment{give number of
 galaxies cut by each criterion?}  Applying these constraints yields a
@@
 the selection criteria; however, only five of these show all
-observations are consistently selected, whereas the other six show one
-or more of the observations did not pass our constraints \comment{we
-should understand why repeat observations are not consistent for the
-majority of cases.  low S/N?}.  \comment{Do this or remove the
-sentence:} Finally, we also visually inspected the broad-band imaging of
-these 790 galaxies and eliminated merging and highly extincted (highly
-inclined) systems yielding a final sample of XXX galaxies.  We hereafter
-refer to galaxies that satisfy our selection criteria as the ``AD
-sample''.
+observations are consistently selected.  The remaining six show one or
+more of the observations did not pass our constraints \comment{we should
+understand why repeat observations are not consistent for the majority
+of cases.  low S/N?}.  \comment{Do this or remove the sentence:}
+Finally, we also visually inspected the broad-band imaging of these 790
+galaxies and eliminated merging and highly extincted (highly inclined)
+systems yielding a final sample of XXX galaxies.  We hereafter refer to
+galaxies that satisfy our selection criteria as the ``AD sample''.
+
+\comment{limitations of an infinitely thin disk fit?}
 
@@
 volume-corrected distribution of the MaNGA parent sample in Mi and N-r,
-and discuss.}
+and discuss?}
 
@@
 $r_s$, of the plotted data with errors derived from $10^3$ bootstrap
-simulations.  We have also used a Markov Chain Monte Carlo
-\comment{refs} to sample the Bayesian posterior distribution for a
-linear regression to the data in each panel, incorporating the errors in
-both axes \comment{refs}; the errors in the kinematic quantities always
-dominate over the absolute magnitude errors.  The fitted model is a line
-in parametric form with an intrinsic Gaussian scatter perpendicular to
-the line.  That is, the line is defined as $\mathbf{l}(t) = \mathbf{l}_0
-+ t\ \hat{\mathbf{l}}$ for a generalized coordinate $t$ along the line,
-an origin $\mathbf{l}_0 = \{x_0, y_0\}$, and the unit vector
-$\hat{\mathbf{l}} = \{\cos\phi, \sin\phi\}$.  The fitted parameters are
-$y_0$, $\phi$, and the dispersion of the intrinsic Gaussian scatter
-about the line, $\varepsilon$; $x_0$ is fixed at the median abscissa of
-the data being fitted ($x_0 = M_{i,0} = -20.6$).  Uniform priors are
-used for $y_0$ and $\phi$ and a logarithmic prior \comment{check this is
-true} is used for $\varepsilon$ \comment{ref}.  Using the returned
-samples of the posterior, we also provide parameters for the
-slope-intercept form of the line --- $y = mx + b$ where $m = \tan\phi$
-and $b = y_0 - x_0 \tan\phi$ --- and the scatter projected along the
-ordinate, $\varepsilon_y = \varepsilon/|\cos\phi$|.  Table
-\ref{tab:lines} provides the median and standard deviation of the
-marginalized distribution of each parameter; these parameters have been
-used to construct the lines provided in Figure \ref{fig:correlation}.
+simulations.  We have also used a Markov Chain Monte Carlo to sample the
+Bayesian posterior distribution for a linear regression to the data in
+each panel, incorporating the errors in both axes \citep[see,
+e.g.][]{2010arXiv1008.4686H}; the errors in the kinematic quantities
+always dominate over the absolute magnitude errors.  The fitted model is
+a line in parametric form with an intrinsic Gaussian scatter
+perpendicular to the line.  That is, the line is defined as
+$\mathbf{l}(t) = \mathbf{l}_0 + t\ \hat{\mathbf{l}}$ for a generalized
+coordinate $t$ along the line, an origin $\mathbf{l}_0 = \{x_0, y_0\}$,
+and the unit vector $\hat{\mathbf{l}} = \{\cos\phi, \sin\phi\}$.  The
+fitted parameters are $y_0$, $\phi$, and the dispersion of the intrinsic
+Gaussian scatter about the line, $\varepsilon$; $x_0$ is fixed at the
+median abscissa of the data being fitted ($M_{i,0} = -20.6$).  Uniform
+priors are used for $y_0$ and $\phi$ and a logarithmic prior
+\comment{check this is true} is used for $\varepsilon$
+\citep{MacKay:itp}.  Using the returned samples of the posterior, we
+also provide parameters for the slope-intercept form of the line --- $y
+= mx + b$ where $m = \tan\phi$ and $b = y_0 - x_0 \tan\phi$ --- and the
+scatter projected along the ordinate, $\varepsilon_y =
+\varepsilon/|\cos\phi$|.  Table \ref{tab:lines} provides the median and
+standard deviation of the marginalized distribution of each parameter;
+these parameters have been used to construct the lines provided in
+Figure \ref{fig:correlation}.
+
+\comment{Show the PDFs?}
 
@@
 and $M_i$.  However, it is important to note that Figure
-\ref{fig:correlation}(b) does not present the Tully-Fisher \comment{ref}
-relation for our AD sample; the Figure gives the rotation speed at
-$R=0.5R_{\rm eff}$, not a measure of the full-width of the dynamically
-broadened line profile.  The slope of the relation in Figure
-\ref{fig:correlation}(b) is steeper than a nominal Tully-Fisher relation
-because galaxies at low luminosity tend to have more slowly rising
-rotation curves \comment{refs}, which can be confirmed by plotting
-$h_{v,{\rm H}\alpha}/R_{\rm eff}$ as a function of $M_i$.
-\comment{actually show this?}
+\ref{fig:correlation}(b) does not present the
+\citet{1977A&A....54..661T} relation for our AD sample; the Figure gives
+the rotation speed at $R=0.5R_{\rm eff}$, not a measure of the
+full-width of the dynamically broadened line profile.  The slope of the
+relation in Figure \ref{fig:correlation}(b) is steeper than a nominal
+Tully-Fisher relation because galaxies at low luminosity tend to have
+more slowly rising rotation curves \comment{refs}, which can be
+confirmed by plotting $h_{v,{\rm H}\alpha}/R_{\rm eff}$ as a function of
+$M_i$.  \comment{actually show this?}
 
@@
 
-If $\sigma_a$ or $v_{{\rm H}\alpha}$ was a secondary parameter in the
-distribution of $(M_i,v_{{\rm H}\alpha})$ or $(M_i,\sigma_a^2)$,
-respectively, we should expect a gradient in the point color in Figures
-\ref{fig:correlation}(b) and \ref{fig:correlation}(c) {\em
-perpendicular} to the fitted regression.  However, we see that the
-primary gradient in point color is parallel to the fitted regression.
-This is consistent with the result that there is little to no
-correlation between $M_i$ and $\sigma_a/v_{{\rm H}\alpha}$, as shown in
-Figure \ref{fig:correlation}(d):  Both $r_s$ and $\phi$ are small and
-only marginally significant with respect to their errors.  From equation
-\ref{eq:dproj}, this implies that the deprojected stellar rotation is a
-roughly constant fraction of the ionized-gas rotation speed, with
-$v_{\ast} \sim 0.9 v_{{\rm H}\alpha}$.  Although the radius at which the
-AD was sampled is different, this ratio is consistent with a similar
-ratio measured for DiskMass-Survey galaxies \comment{Martinsson et al.}.
+If $\sigma_a$ or $v_{{\rm H}\alpha}$ was a fully orthogonal secondary
+parameter in the distribution of $(M_i,v_{{\rm H}\alpha})$ or
+$(M_i,\sigma_a^2)$, respectively, we should expect a gradient in the
+point color in Figures \ref{fig:correlation}(b) and
+\ref{fig:correlation}(c) {\em perpendicular} to the fitted regression.
+However, we see that the primary gradient in point color is parallel to
+the fitted regression.  This is consistent with the result that there is
+little to no correlation between $M_i$ and $\sigma_a/v_{{\rm H}\alpha}$,
+as shown in Figure \ref{fig:correlation}(d):  Both $r_s$ and $\phi$ are
+small and only marginally significant with respect to their errors.
+From equation \ref{eq:dproj}, this implies that the deprojected stellar
+rotation is roughly a constant fraction of the ionized-gas rotation
+speed, with $v_{\ast} \sim 0.9 v_{{\rm H}\alpha}$ \comment{give
+scatter}.  Although the radius at which the AD was sampled is different,
+this ratio is consistent with a similar ratio measured for
+DiskMass-Survey galaxies \citep{2013A&A...557A.130M}.
 
-The points in Figure \ref{fig:correlation}(d) are colored by the global
-$N-r$ color; however, it is difficult to determine from this
-illustration if their is any correlation between $\sigma_a/v_{{\rm
-H}\alpha}$ and global galaxy color.  One might expect such a correlation
-if, for example, galaxies with different global color have different
-light-weightings of the thin vs. thick-disk \comment{refs; not sure
-there are relevant ones; Comer\'{o}n?}, which propagates to a difference
-in which component dominates the dynamical pressure in the disk
-midplane.  Figure \ref{fig:colortrend} assesses this directly by
-plotting the error-weighted mean trend in $\sigma_a/v_{{\rm H}\alpha}$
-for quartiles of the $N-r$ distribution of the AD sample.  The error
-bars represent the error-weighted standard deviation of the data in each
-bin, whereas the error-weighted standard error is always {\it smaller
-than the plotted point}.  This suggests a marginal, yet statistically
-significant, detection of a slightly larger $\sigma_a/v_{{\rm H}\alpha}$
-in the reddest bin.
+\comment{Need to revisit this paragraph in the context of the
+bulge-to-disk fraction.}  The points in Figure \ref{fig:correlation}(d)
+are colored by the global $N-r$ color.  It is difficult to determine
+from this illustration if their is any correlation between
+$\sigma_a/v_{{\rm H}\alpha}$ and global galaxy color.  One might expect
+such a correlation if, for example, galaxies with different global color
+have different light-weightings of the thin- vs. thick-disk
+\comment{refs; not sure there are relevant ones; Comer\'{o}n?}, which
+propagates to a difference in which component dominates the dynamical
+pressure in the disk midplane.  Figure \ref{fig:colortrend} assesses
+this directly by plotting the error-weighted mean trend in
+$\sigma_a/v_{{\rm H}\alpha}$ for quartiles of the $N-r$ distribution of
+the AD sample.  The error bars represent the error-weighted standard
+deviation of the data in each bin, whereas the error-weighted standard
+error is always {\it smaller than the plotted point}.  This suggests a
+marginal, yet statistically significant, detection of a slightly larger
+$\sigma_a/v_{{\rm H}\alpha}$ in the reddest bin.
 

### 2018-04-04 ms.tex
minor updates

@@
 
-\slugcomment{Draft: 14 Feb 2017}
+\slugcomment{Draft: 22 Jan 2018}
 
@@
 
+% Some shorthands
 \newcommand{\kms}{{km$~\!$s$^{-1}$}}
@@
 
-\title{ The trend in asymmetric drift across the blue cloud }
+\title{ Trends in asymmetric drift across the blue cloud }
 
@@
 
-\altaffiltext{1}{UCO/Lick Observatory, University of California, Santa
-Cruz, 1156 High St., Santa Cruz, CA 95064, USA}
+\altaffiltext{1}{University of California Observatories, University of
+California Santa Cruz, 1156 High St., Santa Cruz, CA 95064, USA}
 
-\altaffiltext{2}{Department of Astronomy, University of Wisconsin-Madison, 475
+\altaffiltext{2}{Department of Astronomy, University of Wisconsin--Madison, 475
 N. Charter St., Madison, WI 53706, USA}
@@
 magnitude increase in any galaxy sample size useful for AD measurements.
-In this pilot study, we demonstrate the empirical correlation between
-AD, or more precisely the differential tangential lag between the
-stellar component and \halpha-emitting gas, and global photometric
-properties from the NASA-Sloan Atlas.  We isolate a set of galaxies with
-\halpha\ and stellar velocity fields that are well-fit by simple disk
-models.  Our sample of $\sim$800 galaxies shows a clear correlation
-between absolute $i$-band magnitude and AD measured at half an effective
-radius.  Removing the primary dependence on the rotation speed, we find
-that the stellar disk rotation is 90\% of the \halpha\ rotation speed,
-in the mean.  Our sample size allows us to infer a weak, yet
-statistically significant, trend with galaxy $N-r$ color such that, in
-the mean, redder galaxies have moderately larger AD relative to their
-rotation speeds.  Within the context of an albeit strong set of
-assumptions, including a direct proportionality between AD and stellar
-velocity dispersion as seen in the Milky Way, we argue that our results
-suggest little variation in the mean disk mass-to-light ratio as a
-function of absolute magnitude and only modest variations with galaxy
-color \comment{last sentence TBD; is Figure 3 consistent with SPS
-variations?}.
+In this pilot study, we measure AD --- or more precisely the
+differential tangential lag between the stellar component and
+\halpha-emitting gas --- in a set of galaxies with \halpha\ and stellar
+velocity fields that are well-fit by simple disk models.  We describe
+our fitting approach and the selection of our subsample in detail.  Our
+final sample of $\sim$XXX galaxies shows a clear correlation between
+absolute $i$-band magnitude and AD measured at effectively all radii.
+\comment{The rest neesds to be updated.} Removing the primary dependence
+on the rotation speed, we find that the stellar disk rotation is 90\% of
+the \halpha\ rotation speed, in the mean.  Our sample size allows us to
+infer a weak, yet statistically significant, trend with galaxy $N-r$
+color such that, in the mean, redder galaxies have moderately larger AD
+relative to their rotation speeds.  Within the context of an albeit
+strong set of assumptions, including a direct proportionality between AD
+and stellar velocity dispersion as seen in the Milky Way, we argue that
+our results suggest little variation in the mean disk mass-to-light
+ratio as a function of absolute magnitude and only modest variations
+with galaxy color \comment{last sentence TBD; is Figure 3 consistent
+with SPS variations?}.
 
@@
 4.4.3]{2008gady.book.....B} provide an intuitive description of
-asymmetric drift (AD) as arising due to the combined effect of the
-radially decreasing surface-density and velocity-dispersion profiles
-typical of axisymmetric systems.  Using the $v_R$ moment of the
-collisionless Boltzmann equation, one obtains the Jeans equation
+asymmetric drift (AD).  The combined effect of the radially decreasing
+surface-density and velocity-dispersion profiles, typical of
+axisymmetric systems like the Milky Way, leads to an asymmetric velocity
+distribution function with a mean value less than the circular speed
+defined by the gravitational potential.  The standard mathematical
+representation of this is derived by taking the $v_R$ moment of the
+collisionless Boltzmann equation to find the Jeans equation
 \citep{Jeans1919} that directly relates the circular speed ($v_c$), the
@@
 perpendicular distance to the plane of symmetry --- is negligible
-\citep{1991ApJ...368...79A}.
+\citep[cf.][]{1991ApJ...368...79A}.
 
-Asymmetric drift has been measured in numerous systems.  Perhaps most
-notably, e.g., \comment{Dehnen \& Binney} have shown that populations of
-stars show a direct correlation between their velocity dispersion and
-the degree to which their mean rotation speed lags behind that of the
-Local Standard of Rest (LSR), much in line with the expectation provided
-by equation \ref{eq:adformal}.  Although there have been some studies of
-AD in external galaxies \comment{refs}, it is often treated as a
-nuisance phenomenon that must be corrected for when trying to constrain
-the circular speed of a galaxy \comment{refs}.  The ubiquity and
-phenomenology of AD as a salient observable has not yet been studied for
-a statistically significant population of galaxies.  Our aim is
-therefore to provide a first look at the correlation between AD
-measurements and basic broad-band photometric properties for a large
-sample of galaxies.
+Asymmetric drift has been measured in numerous systems, perhaps most
+notably in the Galaxy.  For example, \citet{1998MNRAS.298..387D} have
+shown that populations of stars show a direct correlation between their
+velocity dispersion and the degree to which their mean rotation speed
+lags behind that of the Local Standard of Rest (LSR), much in line with
+the expectation provided by equation \ref{eq:adformal} (see also
+\comment{more recent RAVE and RAVE+Gaia references}).
+
+Asymmetric drift measurements in extragalactic systems are common in the
+literature \ref{examples}; however, it is most often cast as a nuisance
+phenomenon that one must correct for when constructing circular-speed
+curves \comment{refs}.  The ubiquity and phenomenology of AD as a
+salient observable has not yet been studied for a statistically
+significant population of galaxies.  Our aim is therefore to provide a
+first look at the correlation between AD measurements and basic
+broad-band photometric properties for a large sample of galaxies.
 
@@
 %
-${\rm N} - r$ color and absolute $i$-band magnitude ($M_i$) for all
-galaxies observed during the first two years of the MaNGA Survey (left),
-the subsample of galaxies {\em not} selected to be kinematically regular
-(middle; see text), and the AD sample used throughout the remainder of
-our analysis.  The color of the data points in the top row represent the
-mean \halpha\ surface brightness \comment{check aperture} according to
-the colorbar to the right; the bottom row replaces the color by the
-$r$-band surface brightness density.
+${\rm NUV} - r$ color and absolute $i$-band magnitude ($M_i$) from the
+NASA-Sloan Atlas (NSA) for all galaxies observed during the first two
+years of the MaNGA Survey (left), the subsample of galaxies {\em not}
+selected to be kinematically regular (middle; see text), and the AD
+sample used throughout the remainder of our analysis.  The color of the
+data points in the top row represent the mean \halpha\ surface
+brightness within the elliptical-Petrosian half-light radius according
+to the colorbar to the right; the bottom row replaces the color by the
+mean $g$-band surface brightness density over the same elliptical
+aperture.
 %
@@
 
-In addition to the basic understanding of this dynamically relevant
-quantity, our interest in AD stems from its fundamental dynamical
-connection to the full phase-space distribution function of a galaxy's
-stars, as empirically demonstrated in the Milky Way.  Indeed,
-\citet{2011ApJ...742...18W} used AD to constrain the axial ratios of the
-SVE given direct measurements of the line-of-sight (LOS) stellar
-velocity dispersion, $\sigma$.  Alternatively, if one can leverage
-statistical constraints on the shape of the SVE
-\citep[e.g.][]{2012MNRAS.423.2726G}, measurements of AD can be used as a
-proxy for stellar $\sigma$ via equation \ref{eq:adformal}.  Such a use
-of AD-$\sigma$ relation is attractive in the low-surface-brightness and
-low-velocity-dispersion regimes where direct measurements are difficult
-and/or expensive.  We commit to this paradigm by using the following
-nomenclature for AD, following from equation \ref{eq:adformal}:
-%
-\begin{equation}
-%
-\sigma_a^2 \equiv v_c^2 - \overline{v_\theta}^2.
-%
-\label{eq:addef}
-%
-\end{equation}
+In addition to a basic characterization of the phenomenon, our interest
+in AD stems from its fundamental dynamical connection to the full
+phase-space distribution function of a galaxy's stars, as empirically
+demonstrated in the Milky Way.  Indeed, \citet{2011ApJ...742...18W} used
+AD to constrain the axial ratios of the SVE given direct measurements of
+the line-of-sight (LOS) stellar velocity dispersion, $\sigma$.
+Alternatively, if one can leverage statistical constraints on the shape
+of the SVE \citep[e.g.][]{2012MNRAS.423.2726G}, measurements of AD can
+be used as a proxy for stellar $\sigma$ via equation \ref{eq:adformal}.
+Such a use of AD-$\sigma$ relation is attractive in the
+low-surface-brightness and low-velocity-dispersion regimes where direct
+measurements are difficult and/or expensive.  We commit to this paradigm
+by defining $\sigma_a^2 \equiv v_c^2 - \overline{v_\theta}^2$, following
+from equation \ref{eq:adformal}, for use throughout this paper.
 
@@
 \ion{H}{1}), and/or ionized (\halpha) tracers relative to a robust mass
-model of $v_c$ \comment{Davis et al.}, due to the different
+model of $v_c$ \citep{2013MNRAS.429..534D}, due to the different
 turbulent/thermal pressures intrinsic to these tracers.  However, these
 signatures are much less apparent in disk galaxies.  For example,
-\comment{Martinsson et al.} show that \halpha\ and \ion{H}{1} rotation
+\citet{2013A&A...557A.131M} show that \halpha\ and \ion{H}{1} rotation
 curves are consistent for the DiskMass Survey within the limits of their
-constraints on beam-smearing, suggesting that any correction for the lag
-of either behind the circular speed should be small.  Indeed,
-theoretical calculations \comment{Dalcanton \& Stilp} suggest that
-gas-pressure corrections to \ion{H}{1} rotation curves should be largely
-negligible for galaxies with \comment{${\mathcal M} > 10^x {\mathcal
-M}_\odot$}.  Nevertheless, we emphasize here that our measurements of
-$\sigma_a$ may be better termed as a {\em differential tangential lag}
-because they are based on the quadrature difference between the observed
+constraints on beam-smearing.  This suggests that any correction for the
+lag behind the circular speed of either the \halpha- or
+\ion{H}{1}-emitting gas should be small.  Indeed, theoretical
+calculations \citet{2010ApJ...721..547D} suggest that gas-pressure
+corrections to \ion{H}{1} rotation curves should be largely negligible
+for galaxies with circular speeds larger than roughly 75 \kms.
+Nevertheless, we emphasize here that our measurements of $\sigma_a$ may
+be better termed as a {\em differential tangential lag} because they are
+calculated as the quadrature difference between the {\em observed}
 \halpha\ and stellar rotation curves in our galaxy sample (Section
 \ref{sec:data}).  These measurements are perfectly valid in their own
-right; however, it is their interpretation in the context of the
-theoretical definition of AD that should be questioned in some regimes,
-as discussed in Section \ref{sec:discussion}.
+right; however, their interpretation in the context of the theoretical
+definition of AD must be done with care, as we discuss in Section
+\ref{sec:discussion}.
 
@@
 velocity fields for 2715 unique galaxies, 39 of which have multiple
-observations.  The kinematic measurements are provided by the MaNGA data
-analysis pipeline \comment{DAP; Westfall et al., in prep}: the
-ionized-gas kinematics are based on simple single-Gaussian fits to the
-\halpha\ emission feature and the stellar kinematics are determined
-using {\tt pPXF} (Cappellari et al.) with the MILES stellar template
-library \comment{Jesus FB et al.}.  \comment{Mention hierarchical
-clustering?}
+observations.  These data were obtained during the first two years of
+normal survey operations, and the reduced datacubes are included in DR14
+\citep{2017arXiv170709322A}.  \comment{additional references to
+technical papers}.
 
-The MaNGA galaxy selection \citep{2017AJ....154...86W} is a simple cut
-in absolute $i$-band magnitude, $M_i$, and redshift, $z$, and provides a
-complete sampling of the overall galaxy population.  As such,
+The kinematic measurements are determined by a preliminary version of
+the MaNGA data analysis pipeline (DAP; Westfall et al., in prep).  From
+this preliminary version (2.0.2), we use the simple single-Gaussian fits
+to the \halpha\ emission feature for the ionized-gas kinematics, and the
+stellar kinematics are determined using {\tt pPXF}
+\citep{2004PASP..116..138C, 2017MNRAS.466..798C} with the MILES stellar
+template library \citep{2011A&A...532A..95F}.  We find the velocity
+measurements to be statistically well behaved to a $g$-band
+signal-to-noise ratio (SNR) of $\sim$1.\footnote{
+%
+This and other assessments of the fidelity of the stellar kinematics
+provided by the DAP will be discussed in detail by Westfall et al., {\em
+in prep}.}
+%
+Therefore, we perform our analysis using the stellar kinematics measured
+for each MaNGA spaxel (each spaxel is $0\farcs5$ on a side and
+subsamples the $\sim$$2\farcs5$ fiber beam).
+
+% \comment{Mention hierarchical clustering?}
+
+The MaNGA galaxy selection, see \citet{2017AJ....154...86W}, is a simple
+cut in absolute $i$-band magnitude, $M_i$, from the NASA-Sloan Atlas
+(NSA; \url{www.nsatlas.org}) and the SDSS single-fiber redshift, $z$.
+The MaNGA galaxy sample provides a statistically complete representation
+of the overall galaxy population with a provided set of corrections to a
+volume-limited sample.  The NSA-based ($N-r, M_i$) color-magnitude
+diagram (CMD) of the full sample of galaxies obtained through the second
+year of survey operations are shown in the left-most panels of Figure
+\ref{fig:sample}, with the points colored by the \halpha\ .
+
+Using the photometry from the NSA, Figure \ref{fig:sample} shows the
+color-magnitude diagram of all galaxies colored by their mean \halpha\
+and $r$-band surface brightness.
+
+However, our nominal approach to measuring the stellar and gas rotation curves will be limited forAs such,
 measurements of stellar and/or \halpha\ rotation curves for some systems
-will be difficult/impossible.  Using the photometry from the NASA-Sloan
-Atlas,\footnote{\url{nsatlas.org}} Figure \ref{fig:sample} shows the
-color-magnitude diagram of all galaxies colored by their mean \halpha\
-and $r$-band surface brightness.  \comment{Update this} Although not
+will be difficult/impossible.
+
+\comment{Update this} Although not
 excluded from our velocity-field analysis {\em a priori}, we expect to
@@
 velocity-field fits for all three approaches, (ii) differences in the
-measured \halpha\ and stellar systemic velocity of less than 20 km/s,
+measured \halpha\ and stellar systemic velocity of less than 20 \kms,
 (iii) dynamical centers that are consistent to within a fiber diameter

### 2018-04-30 ms.tex
merge vf fitting

@@
 connection between AD and the stellar phase-space distribution function
-makes it an interesting dynamical properties of galaxies in and of
-itself.  The SDSS-IV/MaNGA survey provides more than an order of
-magnitude increase in any galaxy sample size useful for AD measurements.
-In this pilot study, we measure AD --- or more precisely the
-differential tangential lag between the stellar component and
-\halpha-emitting gas --- in a set of galaxies with \halpha\ and stellar
-velocity fields that are well-fit by simple disk models.  We describe
-our fitting approach and the selection of our subsample in detail.  Our
-final sample of $\sim$XXX galaxies shows a clear correlation between
-absolute $i$-band magnitude and AD measured at effectively all radii.
-\comment{The rest neesds to be updated.} Removing the primary dependence
-on the rotation speed, we find that the stellar disk rotation is 90\% of
-the \halpha\ rotation speed, in the mean.  Our sample size allows us to
-infer a weak, yet statistically significant, trend with galaxy $N-r$
-color such that, in the mean, redder galaxies have moderately larger AD
-relative to their rotation speeds.  Within the context of an albeit
-strong set of assumptions, including a direct proportionality between AD
-and stellar velocity dispersion as seen in the Milky Way, we argue that
-our results suggest little variation in the mean disk mass-to-light
-ratio as a function of absolute magnitude and only modest variations
-with galaxy color \comment{last sentence TBD; is Figure 3 consistent
-with SPS variations?}.
+makes it an interesting dynamical property of galaxies in and of itself.
+The SDSS-IV/MaNGA survey provides more than an order of magnitude
+increase in any galaxy sample size useful for AD measurements.  In this
+pilot study, we measure AD --- or more precisely the differential
+tangential lag between the stellar component and \halpha-emitting gas
+--- in a set of galaxies with \halpha\ and stellar velocity fields that
+are well-fit by simple disk models.  We describe our fitting approach
+and the selection of our subsample in detail.  Our final sample of
+$\sim$XXX galaxies shows a clear correlation between absolute $i$-band
+magnitude and AD measured at effectively all radii.  \comment{The rest
+neesds to be updated.} Removing the primary dependence on the rotation
+speed, we find that the stellar disk rotation is 90\% of the \halpha\
+rotation speed, in the mean.  Our sample size allows us to infer a weak,
+yet statistically significant, trend with galaxy $N-r$ color such that,
+in the mean, redder galaxies have moderately larger AD relative to their
+rotation speeds.  Within the context of an albeit strong set of
+assumptions, including a direct proportionality between AD and stellar
+velocity dispersion as seen in the Milky Way, we argue that our results
+suggest little variation in the mean disk mass-to-light ratio as a
+function of absolute magnitude and only modest variations with galaxy
+color \comment{last sentence TBD; is Figure 3 consistent with SPS
+variations?}.
 
@@
 vertical flows inherent to its derivation, equation \ref{eq:adformal} is
-often simplified by assuming the right-most term --- describing the
-covariance between the radial and vertical motions as a function of
-perpendicular distance to the plane of symmetry --- is negligible
-\citep[cf.][]{1991ApJ...368...79A}.
+often simplified by assuming the right-most term is negligible
+\citep[cf.][]{1991ApJ...368...79A}; i.e., there is negligible covariance
+between the radial and vertical motions as a function of perpendicular
+distance to the plane of symmetry.
 
@@
 Asymmetric drift measurements in extragalactic systems are common in the
-literature \ref{examples}; however, it is most often cast as a nuisance
+literature \comment{examples}; however, it is most often cast as a nuisance
 phenomenon that one must correct for when constructing circular-speed
@@
 the line-of-sight (LOS) stellar velocity dispersion, $\sigma$.
-Alternatively, if one can leverage statistical constraints on the shape
-of the SVE \citep[e.g.][]{2012MNRAS.423.2726G}, measurements of AD can
-be used as a proxy for stellar $\sigma$ via equation \ref{eq:adformal}.
-Such a use of AD-$\sigma$ relation is attractive in the
+Alternatively, if one can statistically constrain the shape of the SVE
+\citep[e.g.][]{2012MNRAS.423.2726G}, measurements of AD could then be
+used as a proxy for stellar $\sigma$ via equation \ref{eq:adformal}.
+Such an AD-$\sigma$ relation becomes attractive in the
 low-surface-brightness and low-velocity-dispersion regimes where direct
-measurements are difficult and/or expensive.  We commit to this paradigm
-by defining $\sigma_a^2 \equiv v_c^2 - \overline{v_\theta}^2$, following
-from equation \ref{eq:adformal}, for use throughout this paper.
+measurements of $\sigma$ are difficult and/or expensive.  Adopting this
+paradigm outright, we define $\sigma_a^2 \equiv v_c^2 -
+\overline{v_\theta}^2$, following from equation \ref{eq:adformal}, for
+use throughout this paper.
 
@@
 directly measure $v_c$, effectively making $\sigma_a$ unobservable.
-That is, every dynamical tracer has some non-zero dynamical pressure
-such that it will lag behind the theoretically defined circular speed.
-There are very clear examples of early-type galaxies that show
-differential AD in their molecular (e.g., CO), atomic (e.g.,
-\ion{H}{1}), and/or ionized (\halpha) tracers relative to a robust mass
-model of $v_c$ \citep{2013MNRAS.429..534D}, due to the different
-turbulent/thermal pressures intrinsic to these tracers.  However, these
-signatures are much less apparent in disk galaxies.  For example,
+That is, every tracer has some non-zero dynamical pressure such that it
+will lag behind the theoretically defined circular speed.  There are
+very clear examples of early-type galaxies that show differential AD in
+their molecular (e.g., CO), atomic (e.g., \ion{H}{1}), and/or ionized
+(\halpha) tracers relative to a robust mass model of $v_c$
+\citep{2013MNRAS.429..534D} due to the different turbulent/thermal
+pressures intrinsic to these tracers.  However, these signatures are
+much less apparent in disk galaxies.  For example,
 \citet{2013A&A...557A.131M} show that \halpha\ and \ion{H}{1} rotation
@@
 
-We present the data used for our analysis in the following section.
-Section \ref{sec:results} presents the strong correlation seen in out
-galaxy sample between the absolute $i$-band magnitude and AD signal
-measured at half of an effective radius (0.5 $R_{\rm eff}$).  We also
-illustrate the weak color dependence in this relation.  Finally, we
-summarize and discuss these results in Section \ref{sec:discussion}.
-\comment{flesh out}
+\comment{Outline should be updated} We present the data used for our
+analysis in the following section.  Section \ref{sec:results} presents
+the strong correlation seen in out galaxy sample between the absolute
+$i$-band magnitude and AD signal measured at half of an effective radius
+(0.5 $R_{\rm eff}$).  We also illustrate the weak color dependence in
+this relation.  Finally, we summarize and discuss these results in
+Section \ref{sec:discussion}.  \comment{flesh out}
 
@@
 \label{sec:data}
+
+\subsection{Galaxy Sample}
 
@@
 
-The kinematic measurements are determined by a preliminary version of
-the MaNGA data analysis pipeline (DAP; Westfall et al., in prep).  From
-this preliminary version (2.0.2), we use the simple single-Gaussian fits
-to the \halpha\ emission feature for the ionized-gas kinematics, and the
-stellar kinematics are determined using {\tt pPXF}
-\citep{2004PASP..116..138C, 2017MNRAS.466..798C} with the MILES stellar
-template library \citep{2011A&A...532A..95F}.  We find the velocity
-measurements to be statistically well behaved to a $g$-band
-signal-to-noise ratio (SNR) of $\sim$1.\footnote{
+The MaNGA galaxy selection is discussed in detail by
+\citet{2017AJ....154...86W}; the galaxies in DR14 represent a random
+sampling of full MaNGA parent sample.  The parent sample is selected
+using simple cuts in absolute $i$-band magnitude, $M_i$, and redshift,
+$z$, from the NASA-Sloan Atlas (NSA; \url{www.nsatlas.org}) to produce
+two main galaxy samples, Primary and Secondary, with roughly twice as
+many galaxies observed from the former.  The main distinguishing
+characteristic of the two samples is MaNGA provides uniform coverage to
+$\sim$$1.5R_e$ and $\sim$$2.5R_e$ for the Primary and Secondary sample,
+respectively.  The Primary sample is supplemented by a
+``Color-enhanced'' sample that improves coverage of the galaxy
+population in low-density regions of color-magnitude space; the
+combination of Primary and Color-enhanced samples are referred to as the
+Primary$+$ sample.  Although we will comment on any difference in our
+analysis results between the Primary$+$ and Secondary samples, we
+largely treat these two samples identically in our analysis.
+
+The ($N-r, M_i$) color-magnitude diagram (CMD) for MaNGA galaxies in
+DR14 (using NSA photometry) is shown in the left-most panels of Figure
+\ref{fig:sample}.  Data in the top and bottom row are colored according
+to, respectively, the average \halpha\ surface brightness and
+$g$-band-weighted mean flux density within 1 $R_e$.  We discuss Figure
+\ref{fig:sample} in the context of our selection of galaxies appropriate
+for our AD analysis \comment{below}.
+
+\subsection{MaNGA Spectroscopy}
+
+The MaNGA fiber-feed system \citet{2015AJ....149...77D} for the
+2.5-meter Sloan telescope at Apache Point Observatory (APO) is coupled
+to the SDSS-III/BOSS spectrographs \citep{2013AJ....146...32S}, a pair
+of dual-channel spectrographs that provide $R_\lambda =
+\lambda/\Delta\lambda \approx 2000$ across the full spectral range of
+$3600\AA \lesssim \lambda \lesssim 10300\AA$.  Each MaNGA pointing
+provides simultaneous observations of 17 galaxies using fiber bundles
+ranging from 19 to 127 fibers.  The dither pattern of the MaNGA
+observational strategy \citep{2015AJ....150...19L} provides a remarkably
+uniform depth for each observation with fields-of-view ranging from
+$12\arcsec$ to $32\arcsec$ for the smallest and largest bundles,
+respectively.  The uniform depth yields a tight correlation between flux
+density per spaxel and signal-to-noise (S/N); see
+\citet{2015AJ....150...19L, 2016AJ....152...83L} and
+\citet{2016AJ....151....8Y, 2016AJ....152..197Y} for additional details
+about the survey execution and performance.
+
+In particular, \citet{2016AJ....152...83L} describes the methods used by
+the MaNGA Data Reduction Pipeline (DRP) is an to produce wavelength-,
+flux- \citep{2016AJ....151....8Y}, and astrometrically calibrated
+spectra from the raw CCD data.  The reduction procedures are similar to
+those used by the SDSS-III/BOSS pipeline, but with significant
+adjustments as required by the MaNGA observations.
+
+Here, we use the rectified datacubes that have been logarithmically
+binned in wavelength (i.e., the \verb|LOGCUBE| files).  The MaNGA data
+cubes are constructed by regridding the flux of all spectra for a given
+plate--IFU combination in each wavelength channel to an on-sky pixel
+(spaxel) sampling of $0\farcs5\times0\farcs5$.  The interpolating PSF
+used in this process is a two-dimensional Gaussian with a standard
+deviation of $0\farcs6$ and a truncation radius of $1\farcs7$.  This
+interpolation process leads to significant covariance between the
+spaxels in a given wavelength channel \citep{2016AJ....152...83L}.  This
+spatial covariance does not affect the primary result of our paper, so
+we defer a more detailed consideration of the covariance for future
+work.
+
+\subsection{Stellar and Ionized-Gas Kinematics}
+
+The kinematic measurements are determined by a preliminary version
+(2.0.2) of the MaNGA Data Analysis Pipeline (DAP; Westfall et al., {\it
+in prep}).  The pipeline provides simple single-Gaussian fits to the
+\halpha\ emission feature that we use for the ionized-gas kinematics,
+and the stellar kinematics are determined using {\tt pPXF}
+\citep{2004PASP..116..138C, 2017MNRAS.466..798C}.  The templates used by
+{\tt pPXF} are a hierarchically clustered distillation of the MILES
+stellar template library \citep{2011A&A...532A..95F}.  We find the
+velocity measurements to be statistically well behaved to a $g$-band
+signal-to-noise ratio of S/N$\sim$1.\footnote{
 %
 This and other assessments of the fidelity of the stellar kinematics
-provided by the DAP will be discussed in detail by Westfall et al., {\em
+provided by the DAP will be discussed in detail by Westfall et al., {\it
 in prep}.}
 %
-Therefore, we perform our analysis using the stellar kinematics measured
-for each MaNGA spaxel (each spaxel is $0\farcs5$ on a side and
-subsamples the $\sim$$2\farcs5$ fiber beam).
+Therefore, we perform our analysis using the spaxel-by-spaxel
+determination of the stellar and ionized-gas kinematics.\footnote{
+%
+However, note that only the stellar kinematic determined for data
+Voronoi binned to S/N$\sim$10 will be provided as part of DR15.}
 
-% \comment{Mention hierarchical clustering?}
+\section{Velocity-Field Modeling}
 
-The MaNGA galaxy selection, see \citet{2017AJ....154...86W}, is a simple
-cut in absolute $i$-band magnitude, $M_i$, from the NASA-Sloan Atlas
-(NSA; \url{www.nsatlas.org}) and the SDSS single-fiber redshift, $z$.
-The MaNGA galaxy sample provides a statistically complete representation
-of the overall galaxy population with a provided set of corrections to a
-volume-limited sample.  The NSA-based ($N-r, M_i$) color-magnitude
-diagram (CMD) of the full sample of galaxies obtained through the second
-year of survey operations are shown in the left-most panels of Figure
-\ref{fig:sample}, with the points colored by the \halpha\ .
+\subsection{Formalism}
 
-Using the photometry from the NSA, Figure \ref{fig:sample} shows the
-color-magnitude diagram of all galaxies colored by their mean \halpha\
-and $r$-band surface brightness.
+We fit the \halpha and stellar velocity fields using an approach similar
+to \citet{2013ApJ...768...41A} \citep[][see also
+\citealt{2011ApJ...742...18W}].  The velocity field is modeled as an
+infinitely thin disk in fully circular rotation that follows a
+parameterized form $V_{\rm rot}(R)$; here we use a simple hyperbolic
+tangent function:
+%
+\begin{equation}
+%
+V_{\rm rot}(R) = V_\infty \tanh(R/h_{\rm rot}),
+%
+\label{eq:tanh}
+%
+\end{equation}
+%
+where $V_\infty$ is the asymptotically flat rotation speed and $h_{\rm
+rot}$ is a characteristic scale for the rise of the rotation curve, and
+the model line-of-sight (LOS) velocity is
+%
+\begin{equation}
+%
+V_{\rm los}(x,y) = V_{\rm rot}(R[x,y])\ \cos(\theta[x,y])\ \sin i +
+V_{\rm sys}
+%
+\label{eq:vlos}
+%
+\end{equation}
+%
+where $i$ is the disk inclination (a ``face-on'' disk has $i=0$), and
+$V_{\rm sys}$ is the systemic velocity of the galaxy.  The disk-plane
+polar coordinates ($R,\theta$) in Equation \ref{eq:vlos} are functions
+of the on-sky position:
+%
+\begin{eqnarray}
+%
+x_d & = & (x+x_0)\sin\phi_0 + (y+y_0)\cos\phi_0 \\
+%
+y_d\cos i  & = & -(x+x_0)\cos\phi_0 + (y+y_0)\sin\phi_0 \\
+%
+R^2 & = & x_d^2 + y_d^2 \\
+%
+\tan\theta & = & -y_d / x_d,
+%
+\label{eq:diskrt}
+%
+\end{eqnarray}
+%
+where ($x,y$) is the on-sky position ($+$$x$ is to the east) relative to
+the center of the object as defined by the targeting catalog,
+($x_0,y_0$) is the location of this pointing center of the IFU relative
+to the dynamical center, $\phi_0$ is the position angle defined from
+north through east of the receding side of the major axis, and
+($x_d,y_d$) are the disk-plane Cartesian coordinates.  Note that
+$\theta=0\arcdeg$ along the major axis on the receding side of the
+galaxy.
 
-However, our nominal approach to measuring the stellar and gas rotation curves will be limited forAs such,
-measurements of stellar and/or \halpha\ rotation curves for some systems
-will be difficult/impossible.
+\comment{REST IS OLD TEXT}
 
-\comment{Update this} Although not
-excluded from our velocity-field analysis {\em a priori}, we expect to
-obtain poor rotation-curve measurements for galaxies with low \halpha\
-and stellar surface brightness.\footnote{
+[[We emphasize that this parametrization is used in the determination of
+the kinematic geometry from the rotation curve, but not as measurements
+of the rotation speed itself (see Section XX).]]
+
+Provided $j=0...N_{\rm spaxels}$ LOS velocity measurements, $V_{{\rm
+los},j}$, and their errors, $\epsilon_{v,j}$, we determine the
+best-fitting model velocity field using a Levenberg-Marquardt
+minimization algorithm with the following figure-of-merit:
 %
-The uniformity of the MaNGA survey \citet{2015AJ....150...19L} is such
-that the signal-to-noise (S/N) of the datacube spaxels is tightly
-correlated with surface brightness.}
+\begin{equation}
+%
+\chi^2 = \sum_j \frac{ (V_{{\rm los},j}-V_{\rm mod}[x_j,y_j])^2 }{
+\epsilon^2_{v,j} + \epsilon^2_{\rm mod}},
+%
+\label{eq:vfchi}
+%
+\end{equation}
+%
+where $\epsilon_{\rm mod}$ is an intrinsic scatter of the measured LOS
+velocities about the simplistic model.  To simplify further discussion,
+we denote the $j$ components of the sum on the right-hand of the
+equation as $\chi^2_j$. [[Go back and include the ``beam-smearing''
+term?]]
 
-\comment{Extinction corrections for the CMD?}
+In an effort to minimize the well-known covariance between the
+inclination and rotation speed (refs), our velocity-field
+parameterization actually fits the {\em projected} rotation curve (i.e.,
+$V_{\rm rot}(R) \sin i$) instead of the disk-plane rotation speed
+itself.  The fitted parameters for a single velocity field are then
+$x_c$, $y_c$, $i$, $\phi_0$, $V_{\rm sys}$, $V_\infty \sin i$, and
+$h_{\rm rot}$.
 
-\comment{Primary vs. Secondary sample?}
+\subsubsection{Implementation details}
+\label{sec:vfimplement}
+
+The description in Section \ref{sec:vfbasic} [[apart from leaving out
+the beam-smearing term]] is identical to the approach of
+\citet{2013ApJ...768...41A}.  The alterations specific to our
+implementation are as follows \citep[cf.][]{2011ApJ...742...18W}:
+
+\begin{enumerate}
+%
+\item {\em Simultaneous VF fitting}:  We have extended the code from
+\citet{2013ApJ...768...41A} to allow for simultaneous fits to multiple
+dynamical tracers, while allowing the rotation curves of the two
+components to be different.  Although we do fit the \halpha and stellar
+data fit independently, this is primarily used in the selection cuts
+imposed in Section \ref{sec:kingeomcuts}.  When fitted simultaneously,
+there are three additional free parameters compared to those listed
+above: the two additional rotation curve parameters and systemic
+velocity of the second dynamical tracer.  That is, even when fitting the
+two velocity fields simultaneously, we allow for the systemic velocities
+of the two tracers to be different.  This is primarily to allow for,
+e.g., systematic errors in the velocity registration of the template
+libraries used to determine the stellar kinematics.  Ideally, one would
+like to force the systemic velocities of the two tracers to be the same,
+and we discuss the effects on our results by allowing them to be
+different in Section \ref{sec:kingeom}.
+%
+\item{\em Intrinsic scatter}:  The intrinsic scatter term,
+$\epsilon_{\rm mod}$, serves a number of purposes.  Its effect is to
+alter the error-weighted distribution of the fit residuals such that it
+closely follows a Gaussian distribution with unity standard deviation;
+that is, it forces the reduced $\chi^2$, $\chi^2_\nu$, of the fit to be
+very close to unity.  Indeed, \citet{2013ApJ...768...41A} chose
+$\epsilon_{\rm mod}$ such that $\chi^2_\nu$$\sim$1 to within 1\%.  Our
+approach is to instead iteratively adjust $\epsilon_{\rm mod}$ until the
+growth curve of $\chi^2_j$ is marginally different from the growth curve
+of a Gaussian function with unity standard deviation.  This approach is
+primarily chosen given its advantage in dealing with our third
+alteration. [[Affect on formal parameter errors from the covariance
+matrix.]]
+%
+\item{\em Measurement Rejection}:  The fits to the velocity fields
+generally provide $\chi^2_\nu > 1$ when $\epsilon_{\rm mod} = 0$,
+meaning that there is a general systematic discrepancy of model with
+respect to the $V_{\rm los}$ measurements that is not accounted for by
+the random errors, $\epsilon_{v,j}$.  Although most of the discrepancies
+can be accounted for by a small ($\epsilon_{\rm mod}\sim XX$) scatter
+about the simplistic model, systematic error in the kinematic
+measurements, particularly at low SNR, can lead to a number of
+$V_{{\rm los},j}$ with $\chi^2_j \gg 1$.  We iteratively reject these
+data from the fit at the same time as we determine the intrinsic scatter
+term, $\epsilon_{\rm mod}$.  After fitting the data with a given
+$\epsilon_{\rm mod}$ (starting with 0), we iteratively reject points
+with $\chi^2_j > 1$, starting with the largest value, and adjust
+$\epsilon_{\rm mod}$ until the root-mean-square difference between the
+growth curve of $\chi^2_j$ and a Gaussian with unity standard deviation
+is minimized.  This whole process of fitting the velocity field,
+determining $\epsilon_{\rm mod}$, and rejecting aberrant data is done
+many times to make sure that the points that are rejected and the value
+of $\epsilon_{\rm mod}$ is not strongly biased by the initial fit to the
+velocity field.
+%
+\end{enumerate}
+
+% [[I realize that the above two (maybe even all three) things are
+% highly detailed.  We probably want to make them simpler.]]
+
+\subsubsection{Initialization}
+\label{sec:vfinit}
+
+The MaNGA data cubes (cf. Law et al.~{\em in prep}) provide an accurate
+registration of the spectrophotometry with on-sky imaging data to
+provide a detailed astrometric calibration in the form of a
+world-coordinate system (WCS) in the fits headers. The coordinates of
+the targeted galaxy\footnote{
+%
+This is generally the center of the data cube field-of-view; however,
+some observations were purposely offset for testing purposes.
+%
+} are, in general, exactly the coordinates provided by the NASA-Sloan
+Atlas; however, some coordinates have been adjusted to better match the
+galaxy center [[check this with David W.]] (cf., Wake et al.~{\em in
+prep}).  The ($x,y$) coordinate system in Eqn. \ref{eq:vlos} is then
+established by setting the (0,0) coordinate at the galaxy center.  Thus,
+when freely fit, we should expect to find $x_0 = y_0 = 0$ arcsec.
+
+The NASA-Sloan Atlas also provides ellipticity and position angle
+measurements for isophotal contours of each galaxy, which we use as the
+initial guesses for the kinematic inclination and position angle,
+respectively.  For an oblate spheroid with intrinsic axial ratio $q_0$
+and an observed ellipticity of $\varepsilon = 1-b/a$, its inclination to
+the LOS is given by (ref)
+%
+\begin{equation}
+%
+\cos^2 i_{\rm phot} = \frac{ (1-\varepsilon)^2 - q_0^2 }{ 1 - q_0^2 }.
+%
+\label{eq:inc}
+%
+\end{equation}
+%
+For our measurements of $i_{\rm phot}$, we assume $q_0 = 1/8$ (Bershady;
+but, cf., Weijmanns).
+
+Given that our definition of $\phi_0$ is tied to the vector along the
+major axis toward the receding side of the velocity field, the kinematic
+position angle has a valid range of $2\pi$.  However, photometric
+position angles only have a valid range of $\pi$.  Our initial guess of
+$\phi_0$ is either the same as the photometric value or flipped by
+$180\degr$ based on an initial deprojection of the rotation speed along
+the photometric position angle.
+
+Finally, we use the redshift provided by the NASA-Sloan Atlas as the
+initial estimate of the systemic velocity, $V_{\rm sys} = c z_{\rm
+NSA}$.
+
+\subsubsection{Fitting iterations}
+\label{sec:vfiter}
+
+We expect AD to be present in all galaxies, and so we
+attempt to fit all 1392 galaxies in the current MaNGA sample.  For such
+a large galaxy sample, it is difficult to attempt human interaction at a
+detailed level with each fit.  Therefore, all of the fits have been
+performed in an automated way.  To help in the quality assessments of
+the fits (Sections \ref{sec:kingeom} and \ref{sec:kingeomcuts}), we fit
+the velocity fields of each tracer (\halpha-emitting gas and stars) both
+individually and in a single, simultaneous fit.  Additionally, we
+perform the individual and simultaneous fits under permutations of
+fixing and freeing the inclination and center.
+
+The determination of $V_{\rm sys}$ and $\phi_0$ are generally robust and
+well-constrained by the data, meaning there is no need to fix them to
+certain values.  Conversely, the inclination and center can be poorly
+determined in certain regimes.  For example, when the observed velocity
+field is that of a solid-body rotator, the isovelocity contours all
+become parallel to the minor axis ($V_{\rm rot} \propto R$ and, at a
+fixed perpendicular distance from the minor axis, $\cos\theta \propto
+R^{-1}$).  Thus, in the absence of any other information, one could
+place the center anywhere in the velocity field without affecting
+$\chi^2$.  Similarly, measurements of inclination depend on the
+curvature seen in the isovelocity contours and there is no such
+curvature for a solid-body rotator.  Finally, at low inclination, the
+curvature in the isovelocity contours can be imperceptible due to the
+stochastic deviations (random and systematic) about the fitted model.
+Therefore, by performing fits that both fix and free the center and
+inclination, we can test the consistency of the results and the
+significance of kinematically constrained parameters versus simply
+adopting the photometric one.
+
+In addition, we impose boundaries on the allowed range for the geometric
+parameters.  We force the systemic velocity to be within $\pm1000$
+\kms{} of the input guess, we force $0.1\leq i \leq 85$ and
+$0\leq\phi_0<360$, and we define a bounding box for the fitted center to
+be $\sim$20\% of the full field-of-view.  The limits for the IFUs with
+19, 37, 61, 91, and 127 fibers are limited to $\pm1\arcsec$,
+$\pm2\arcsec$, $\pm2\arcsec$, $\pm3\arcsec$, and $\pm3\arcsec$,
+respectively.
+
+In summary, we perform 12 velocity-field fits for each galaxy: (1) four
+fits are permutations of fixing and freeing the center and inclination
+and (2) each of these four fits is done when only fitting the \halpha
+data, only fitting the stellar data, and fitting both tracers
+simultaneously.
+%
+\begin{figure*}
+%
+\includegraphics[width=0.9\textwidth]{figs/sys_cen_pa.pdf}
+%
+\caption{
+%
+Distribution of (a) the difference between the \halpha and stellar
+systemic velocities; (b) the center relative to the imposed fit
+boundary; and (c) the difference between the \halpha and stellar kinematic
+position angles.  For the center panel, the distributions of
+$\tilde{x}_0$ and $\tilde{y}_0$ are shown as (transparent) light and
+dark histograms, respectively.  The 3-sigma clipped mean ($\mu$) and
+standard deviation ($\epsilon$) for each distribution is provided in
+associated panel.  The dashed lines illustrate the cuts that we adopt
+for each parameter in our AD analysis(see text).
+%
+}
+%
+\label{fig:sys_cen_pa_hist}
+%
+\end{figure*}
+
+\subsection{Kinematic Geometry Results}
+\label{sec:kingeom}
+
+For our AD measurements, we require robustly measured kinematic
+geometries that can be applied to both the \halpha-emitting and stellar
+components.  This requirement drives our assessments of the kinematic
+geometries and the selection of galaxies to propagate through our AD
+analysis in the remaining sections of the paper.  For example, it is
+physically plausible to find a significant offsets between the position
+angles of gas and stars (e.g., Chen et al.; Belfiore et al.); however,
+this is typically the signature of an accretion event and not conducive
+to an AD measurement.  Given the fits that we have performed, we can
+check both the consistency of the \halpha and stellar geometries, as well
+as their consistency with the morphological geometry.
+
+We first limit our assessments to those galaxies with successfully
+converged velocity-field fits for all 12 fit iterations, which cuts our
+sample from 1392 to 1322 galaxies.  [[Should maybe have a sentence about
+why these failed?]]  All subsequent cuts include this base-level
+selection.
+
+\subsubsection{Systemic velocity}
+
+When fit separately, the best-fitting systemic velocities for both the
+\halpha and stellar data are in good agreement with each other and with
+the redshifts in the NASA-Sloan Atlas, $cz_{\rm NSA}$.  The mean
+difference with respect to $cz_{\rm NSA}$ over the full 1322 galaxies is
+less than 10 \kms{} and the standard deviation is approximately the
+velocity width of a spectral channel ($\sim$70 \kms{}), regardless of
+the fitting constraints or tracer.
+
+The result is approximately the same when considering the difference
+between the \halpha-only and stellar-only fit parameters.  Indeed, we
+should expect that the systemic velocity should be the same for the
+\halpha and stellar components; however, we have allowed them to be
+different, even when fitting the two velocity fields simultaneously.
+Fig.~\ref{fig:sys_cen_pa_hist}(a) shows the distribution of $V_{{\rm
+sys,H}\alpha} - V_{{\rm sys},\ast}$ when both are fit simultaneously.
+After applying a 3-sigma clipping algorithm, we find a mean difference
+of $2.3\pm6.8$ \kms{}.  It is difficult to understand how this
+systematic offset could arise either physically or due to a
+wavelength-calibration error.  We therefore assume that this mean offset
+is due to a systematic error in the velocity registration of the MIUSCAT
+template spectra across our fitted wavelength range.  Further work is
+required to exactly address this problem; however, it has a minimal
+effect on our analysis [[need to test this]].
+
+To avoid the strong outliers, particular toward the negative end of
+Fig.~\ref{fig:sys_cen_pa_hist}(a), we select only those galaxies with
+-12.5 \kms{} $\leq V_{{\rm sys,H}\alpha} - V_{{\rm sys},\ast} \leq 17.5$
+\kms{} for further analysis; 850 of 1322 galaxies (64\%) meet this
+criterion.
+
+\subsubsection{Pointing relative to the dynamical center}
+
+In Section \ref{sec:vfiter}, we noted that the pointing relative to the
+dynamical center ($x_0,y_0$) has a bounding box placed on it that is
+IFU-dependent.  When selecting results for our AD analysis, we care more
+about the fitted center relative to the bounding box than we do about
+the absolute center in arcseconds.  Therefore, in
+Fig.~\ref{fig:sys_cen_pa_hist}(b) we show the ratio of the fitted center
+relative to the size of the bounding box --- e.g., $-1\leq \tilde{x}_0
+\leq 1$ --- for both on-sky coordinates.  Recall (Section
+\ref{sec:vfbasic}) the definition of our ($x,y$) coordinate system is
+such that a result of $(x_0,y_0) = (0,0)$ means that the morphological
+and dynamical centers are co-located.
+
+The results in Fig.~\ref{fig:sys_cen_pa_hist}(b) are specifically for
+the case where we have fit both tracers simultaneously.  We find that
+the simultaneous fit to both tracers reduces the scatter about the
+morphological center compared to the result for the fits to an
+individual tracer: the standard deviations are 0.52, 0.44, and 0.39 for
+the \halpha, stellar, and combined fits, respectively.  Under the
+expectation that the morphological and dynamical centers should be the
+same for dynamically settled galaxies, we force both $\tilde{x}_0$ and
+$\tilde{y}_0$ to be within $\pm0.5$, of which 926/1322 (70\%) of the
+galaxies satisfy.  Before applying this selection, the standard
+deviation of $(x_0,y_0)$ is approximately $0\farcs9$ for each
+coordinate, which is reduced by a factor of 3 for the selected sample of
+926 galaxies.
+
+\subsubsection{Position angle}
+
+The kinematic position angle is periodic with an imposed range in the
+fit of $0\leq\phi_0\leq360$.  In calculating the difference between any
+two position angles, we account for this range and periodicity such that
+the difference in position angle should be centered at $0\degr$, as is
+the case when comparing $\phi_{0,{\rm H}\alpha}$ and $\phi_{0,\ast}$ in
+Fig.~\ref{fig:sys_cen_pa_hist}(c).  Although physical differences in the
+fitted position angles are interesting for other reasons (earlier refs;
+Chen et al.; Belfiore et al.), our measurements of AD benefit from
+selecting galaxies where the position angles are very similar.
+
+In contrast with the other two panels in Fig.~\ref{fig:sys_cen_pa_hist},
+panel (c) compares the results when each dynamical tracer is fit
+independently.  We find a standard deviation in the difference of
+$7\degr$ after iteratively clipping at 3-sigma.  We have chosen to
+select only those galaxies with \halpha and stellar derived $\phi_0$ that
+differ by less than $15\degr$, which selects 832 of the 1322 (63\%)
+galaxies.  Although our selection criterion for $\phi_0$ is based on the
+\halpha-only and stellar-only fits, we note that the calculation of AD
+{\em assumes the position angle obtained from the simultaneous fit to
+both tracers}.  The 3-sigma clipped standard deviation of the difference
+between $\phi_{0,{\rm H}\alpha}$ or $\phi_{0,\ast}$ and the result when
+both are fit simultaneously is $\sim$1$\degr$.
+
+\begin{figure}
+%
+\includegraphics[width=0.98\columnwidth]{figs/inc_select.pdf}
+%
+\caption{
+%
+Comparison of the three kinematic inclinations --- as resulting from the
+\halpha-only ($i_{{\rm H}\alpha}$), stellar-only ($i_\ast$) and
+simultaneous ($i_{\ast+{\rm H}\alpha}$) fits --- with the photometric
+inclination, $i_{\rm phot}$ (see eqn.~\ref{eq:inc}).  From top-left to
+bottom-right, the panels illustrate the progression of our
+inclination-based selection criteria.  The gray dotted line shows the
+1:1 correspondence in all panels.  ({\em Top row}): Comparison of
+$i_{\ast+{\rm H}\alpha}$ (abscissa) and $i_\ast$ (ordinate) for all 1322
+galaxies with successful velocity-field fits.  The top-left panel shows
+the distribution before any selection criteria are applied, whereas the
+top-right panel converts the point type for galaxies that are {\em not}
+selected by the constraints on $V_{\rm sys}$, $(x_0,y_0)$, and $\phi_0$
+to small points.  In the top-right panel, the dashed polygon represents
+our primary inclination criterion.  ({\em Bottom row}): Comparison of
+$i_{\rm phot}$ (abscissa) with $i_{\ast+{\rm H}\alpha}$ (ordinate);
+large dots and small points have the same meaning as in the top-right
+panel.  The bottom-left panel shows all galaxies that pass our primary
+inclination criterion, whereas the bottom-right panel shows only those
+galaxies that satisfy both criteria (see text).  The dashed lines in the
+bottom-left panel illustrate our secondary inclination criterion.
+%
+}
+%
+\label{fig:incselect}
+%
+\end{figure}
+
+\subsubsection{Inclination}
+
+In Fig.~\ref{fig:incselect}, we compare the photometric inclinations
+(see eqn.~\ref{eq:inc}) with the kinematic inclinations determined from
+the \halpha-only ($i_{{\rm H}\alpha}$), stellar-only ($i_\ast$), and
+simultaneous ($i_{\ast+{\rm H}\alpha}$) velocity-field fits,
+illustrating the progression of our inclination selection criteria.
+
+The top-left panel of Fig.~\ref{fig:incselect} shows that the fitted
+inclinations for a significant number of galaxies are biased by our
+imposed fit boundaries.  Therefore, we first only consider galaxies with
+kinematic inclinations that are between $15\degr < i_{\rm kin} <
+80\degr$.  Even after imposing this limit, however, we find $i_{{\rm
+H}\alpha} - i_\ast \approx -1\degr\pm16\degr$.  The difference between
+$i_{\ast+{\rm H}\alpha}$ and either $i_{{\rm H}\alpha}$ or $i_\ast$ has
+an understandably smaller scatter of $\pm11\degr$.  If we simultaneously
+impose the constraints outlined above for $V_{\rm sys}$, $(x_0,y_0)$,
+and $\phi_0$, we are left with 622 of 1322 galaxies that have $i_{{\rm
+H}\alpha} - i_\ast \approx -2\degr\pm12\degr$, as shown in the top-right
+panel of Fig.~\ref{fig:incselect}.  Based on this distribution, our
+primary inclination selection is $15\degr < i_{\rm kin} < 80\degr$ and
+$|i_{{\rm H}\alpha} - i_\ast| < 20\degr$.  When applied to fits both
+with and without the center fixed, the criterion is satisfied by 524 of
+the 1322 galaxies.
+
+Our secondary criterion checks for consistency of $i_{\ast+{\rm
+H}\alpha}$ and $i_{\rm phot}$, which is shown in the bottom-left panel
+of Fig.~\ref{fig:incselect}.  After imposing only the primary
+inclination criterion, we find $i_{\ast+{\rm H}\alpha} - i_{\rm phot} =
+0\degr\pm10\degr$; the scatter decreases to $\pm9\degr$ if we also apply
+the $V_{\rm sys}$, $(x_0,y_0)$, and $\phi_0$ criteria.  Our secondary
+inclination criterion imposes $|i_{\ast+{\rm H}\alpha} - i_{\rm phot}| <
+20\degr$, such that the full sample is shown as filled dots in the
+bottom-right panel of Fig.~\ref{fig:incselect}.  The combination of the
+two inclination criteria yields our most stringent selection cut,
+limiting our sample from 1322 to 487 galaxies.
+
+% Since our goal is to measure asymmetric drift, we want to force the
+% kinematic geometry fitted to the \halpha and stellar velocity fields to
+% be identical; however, we want to allow for the rotation curves of the
+% two tracers to be independent.
+
+[[Note the systematic offset between the kinematic and photometric
+inclinations at $i_{\rm phot} \gtrsim 60\degr$.  Known inadequacy of the
+infinitely thin model.  Check the effect this has on the AD-$\sigma$
+distribution.]]
+
+\subsubsection{Summary of selection cuts}
+\label{sec:kingeomcuts}
+
+In summary, our AD-$\sigma$ analysis is of galaxies that satisfy the
+following set of constraints on the results from the velocity field
+fitting:
+%
+\begin{enumerate}
+%
+\item When the two velocity fields are fitted simultaneously, the
+difference between the systemic velocities fit to the \halpha and stellar
+velocity fields must be within -12.5 \kms{} $\leq V_{{\rm
+sys,H}\alpha}-V_{{\rm sys},\ast} \leq 17.5$ \kms{} for {\em all} four of
+the fit permutations.
+%
+\item In the two simultaneous fits to the \halpha and stellar data with
+the dynamical center left free, the dynamical center must be within half
+of the imposed bounding box on the morphological center.
+%
+\item For {\em all} the relevant fit permutations, the difference
+between the \halpha-only and stellar-only fitted position angles must be
+less than 15$\degr$.
+%
+\item In {\em all} six fits when the inclination is freely fit, the
+best-fitting kinematic inclination must be in the range $15\degr <
+i_{\rm kin} < 80\degr$.  The difference between the \halpha-only and
+stellar only kinematic inclinations must be less than $20\degr$ both
+with and without a fixed center.  When both tracers are fit
+simultaneously, the kinematic inclination must also be within $20\degr$
+of the photometric inclination (eqn.~\ref{eq:inc}).
+%
+\end{enumerate}
+%
+The simultaneous application of all these cuts yields a sample of 413
+galaxies from the original set of 1322.
+
+% (Under the expectation that a similar fraction applies to the full
+% MaNGA sample, we should be able to obtain a sample of $\sim$3000
+% galaxies for AD measurements in 2020!)
+
+% \subsection{Uncertainties}
+% \label{sec:vfuncer}
+% 
+% \subsubsection{Beam smearing}
+% \label{sec:vfbeam}
+% 
+% [Test by constructing some models?]
+% 
+% \subsubsection{Template Effects}
+% \label{sec:vftpl}
+% 
+% (Brief) comparison of MILES and MIUSCAT results.
+% 
+% \subsubsection{Covariance}
+% \label{sec:vfcov}
 
@@
 %\end{deluxetable*}
+
+Using the photometry from the NSA, Figure \ref{fig:sample} shows the
+color-magnitude diagram of all galaxies colored by their mean \halpha\
+and $r$-band surface brightness.
+
+However, our nominal approach to measuring the stellar and gas rotation curves will be limited forAs such,
+measurements of stellar and/or \halpha\ rotation curves for some systems
+will be difficult/impossible.
+
+\comment{Update this} Although not
+excluded from our velocity-field analysis {\em a priori}, we expect to
+obtain poor rotation-curve measurements for galaxies with low \halpha\
+and stellar surface brightness.
+
+\comment{Extinction corrections for the CMD?}
+
+\comment{Primary vs. Secondary sample?}
